---
title: "Data Analysis for Researchers 2023, Week 5"
author: "Hiroshi Suzuki"
date: "2024/01/24"
output:
  html_notebook: default
  ioslides_presentation:
    widescreen: yes
  html_document:
    df_print: paged
---

# Part I: EDA with Public Data

## Preview

-   Week 5, Jan. 24: EDA4, UN, OECD, readr, readxl, two table verves, modeling

-   Week 6, Jan. 31: EDA5, Round-up, communication, pdf, Word, PowerPoint

### Directory and Folder

*Q. Explain the difference between the directory and the folder of PC briefly.*

*A. by Bard.*

Here's a brief explanation of the differences between directories and folders on a PC:

Directory (Technical Term):

-   Fundamental file system structure: It's the way your computer organizes files and folders in a hierarchical structure.

-   Can contain files, subdirectories, and even other directories.

-   Abstract concept: It's not directly visible in graphical user interfaces (GUIs) like Windows Explorer.

-   Referred to in command-line interfaces (CLIs) like the Terminal.

Folder (Visual Metaphor):

-   Graphical representation of a directory: It's the icon you see in your file explorer.

-   User-friendly way to interact with directories: It allows you to create, move, rename, and delete them.

-   May contain files and other folders (subfolders).

-   Common term in GUIs: It's what most people interact with on a daily basis.

Key Points:

-   Directories are the underlying structure, while folders are visual representations.

-   They're often used interchangeably in casual conversation.

-   Technical discussions often use "directory" for accuracy.

-   Both terms refer to a way to organize files on your computer.

------------------------------------------------------------------------

### Where are you in R? - Working Directory 

-   The directory of a folder and a file under Files:

    -   Shown under Files starting from a house icon.

-   Working directory of your project:

    -   Run `getwd()` in Console.

-   Working directory of your RNotebook:

    -   Run `getwd()` in a code chunk.

    -   The directory your *`file_name.Rmd`* and *`file_name.nb.html`* is.

-   Confirm `data` folder is in the working directory of your RNotebook.

```{r}
getwd()
```

## Importing Data

### Data Location

-   Internet link: URL

    -   link of the webpage, other information

    -   `download.files(url, destifile = "data/name_of_data.XXX", mode = "wb")`

        -   `mode = "wb"` for digital files

        -   .XXX: extenstions; csv, tsv, xls, xlsx

-   `data` folder: downloaded or created data

    -   link of the webpage, other information

#### Reproducibility

Keep a record of the data so that you can communicate with others how to obtain the data.

### File Types

-   Text file: CSV, etc

-   Digital file: Excel, etc

-   Other: archived compressed file, json, etc.

    -   unzip or expand first

    -   may contain many files; data, metadata, readme, etc.

### **Importing text data**

-   `readr`: a part of `tidyverse`

    -   [`read_csv()`](https://readr.tidyverse.org/reference/read_delim.html): comma-separated values (CSV)

    -   [`read_tsv()`](https://readr.tidyverse.org/reference/read_delim.html): tab-separated values (TSV)

    -   [`read_csv2()`](https://readr.tidyverse.org/reference/read_delim.html): semicolon-separated values with `,` as the decimal mark

    -   [`read_delim()`](https://readr.tidyverse.org/reference/read_delim.html): delimited files (CSV and TSV are important special cases)

    -   [`read_fwf()`](https://readr.tidyverse.org/reference/read_fwf.html): fixed-width files

    -   [`read_table()`](https://readr.tidyverse.org/reference/read_table.html): whitespace-separated files

    -   [`read_log()`](https://readr.tidyverse.org/reference/read_log.html): web log files

    -   例：`df_name <- read_csv("data/datafile.csv")`

-   Reference

    -   [readr site](https://readr.tidyverse.org/) 

    -   Data Importing CheatSheet

### **Excel files (xls, xlsx)**

-   readxl: a part of tidyverse but you need to load by [`library(readxl)`](https://readxl.tidyverse.org/) 

    -   `df_name <- read_excel("./data/datafile.xlsx")`

    -   `read_xls` and `read_xlsx` are available

    -   `sheet = 2`, or `sheet = "name"`

-   file import of RStudio

-   Reference

    -   [readxl](https://readxl.tidyverse.org/) 

    -   Data Importing CheatSheet

### **Download data file**

-   text file (csv, etc.)

    -   `download.file(url = "URL", destfile = "./data/file_name.csv")`

    -   `df_name <- read_csv(URL)`

        -   `write_csv(df_name, "./data/df_name.csv")`

        -   `df_name <- read_csv("./data/df_name.csv")`

-   digital file (Excel)：`download.file(url = "URL", destfile = "./data/file_name.xlsx", mode = "wb")`

-   eg

```{r}
library(tidyverse)
```

```{r}
url_summary <- "https://wir2022.wid.world/www-site/uploads/2022/03/WIR2022TablesFigures-Summary.xlsx"
download.file(url = url_summary, destfile = "./data/WIR2022s.xlsx", mode = "wb")
```

```{r}
url_un_migrants <- "https://data.un.org/_Docs/SYB/CSV/SYB66_327_202310_International%20Migrants%20and%20Refugees.csv"
```

```{r}
df_un_migrants <- read_csv(url_un_migrants, skip = 1)
df_un_migrants
```

```{r}
str(df_un_migrants)
```

Download data

```{r}
download.file(url_un_migrants, destfile = "data/un_migrants.csv")
```

```{r}
df_un_migrants |> summary()
```

```{r}
df_un_migrants |> select(Year,Series) |> lapply(unique)
```

```{r}
df_un_migrants |> distinct(`Region/Country/Area`, ...2)
```

```{r}
library(countrycode)
df_un_migrants %>% mutate(iso2c_un = countrycode(`Region/Country/Area`, "un", "iso2c"), .after = ...2)
```

```{r}
df_un_migrants |> mutate(iso2c_un = countrycode(`Region/Country/Area`, "un", "iso2c"), .after = ...2) |> filter(is.na(iso2c_un)) |> distinct(...2)
```

```{r}
wdicache <- read_rds("data/wdicache.rds")
wdi_country_extra <- wdicache$country |> select(iso2c, region, income, lending)
```

```{r}
df_un_migrants_ext <- df_un_migrants %>% 
  mutate(iso2c_un = countrycode(`Region/Country/Area`, "un", "iso2c"), .after = ...2) |>
  drop_na(iso2c_un) |> 
  select(Country = ...2, ISO2C = iso2c_un, Year, Series, Value, Footnotes) |>
  left_join(wdi_country_extra, by = c("ISO2C" = "iso2c"))
df_un_migrants_ext
```

```{r}
df_un_migrants_ext$Series |> unique()
```

```{r}
df_un_migrants_ext_rev <- df_un_migrants_ext |> mutate(Ser = case_when(
  Series == "International migrant stock: Both sexes (number)" ~ "migrant",
  Series == "International migrant stock: Both sexes (% total population)" ~ "migrant_percent",
  Series == "International migrant stock: Male (% total Population)" ~ "migrant_male",
  Series == "International migrant stock: Female (% total Population)" ~ "migrant_female",
  Series == "Total refugees and people in refugee-like situations (number)" ~ "refugee",
  Series == "Asylum seekers, including pending cases (number)" ~ "asylum",
  Series == "Other of concern to UNHCR (number)"  ~ "other",
  Series == "Total population of concern to UNHCR (number)" ~ "concern",
  TRUE ~ Series), .before = Series)
df_un_migrants_ext_rev
```

```{r}
dput(df_un_migrants_ext_rev)
```

```{r}
df <- structure(list(Country = c("Afghanistan", "Afghanistan", "Afghanistan", 
"Afghanistan", "Afghanistan", "Afghanistan", "Afghanistan", "Afghanistan", 
"Afghanistan", "Afghanistan", "Afghanistan", "Afghanistan", "Afghanistan", 
"Afghanistan", "Afghanistan", "Afghanistan", "Afghanistan", "Afghanistan", 
"Afghanistan", "Afghanistan", "Afghanistan", "Afghanistan", "Afghanistan", 
"Afghanistan", "Afghanistan", "Afghanistan", "Afghanistan", "Afghanistan", 
"Afghanistan", "Afghanistan", "Afghanistan", "Afghanistan", "Afghanistan", 
"Afghanistan", "Afghanistan", "Afghanistan", "Albania", "Albania", 
"Albania", "Albania", "Albania", "Albania", "Albania", "Albania", 
"Albania", "Albania", "Albania", "Albania", "Albania", "Albania", 
"Albania", "Albania", "Albania", "Albania", "Albania", "Albania", 
"Albania", "Albania", "Albania", "Albania", "Albania", "Albania", 
"Albania", "Albania", "Albania", "Albania", "Albania", "Albania", 
"Albania", "Albania", "Albania", "Algeria", "Algeria", "Algeria", 
"Algeria", "Algeria", "Algeria", "Algeria", "Algeria", "Algeria", 
"Algeria", "Algeria", "Algeria", "Algeria", "Algeria", "Algeria", 
"Algeria", "Algeria", "Algeria", "Algeria", "Algeria", "Algeria", 
"Algeria", "Algeria", "Algeria", "Algeria", "Algeria", "Algeria", 
"Algeria", "Algeria", "Algeria", "Algeria", "American Samoa", 
"American Samoa", "American Samoa", "American Samoa", "American Samoa", 
"American Samoa", "American Samoa", "American Samoa", "Andorra", 
"Andorra", "Andorra", "Andorra", "Andorra", "Andorra", "Andorra", 
"Andorra", "Angola", "Angola", "Angola", "Angola", "Angola", 
"Angola", "Angola", "Angola", "Angola", "Angola", "Angola", "Angola", 
"Angola", "Angola", "Angola", "Angola", "Angola", "Angola", "Angola", 
"Angola", "Angola", "Angola", "Angola", "Angola", "Angola", "Angola", 
"Angola", "Angola", "Angola", "Angola", "Angola", "Angola", "Angola", 
"Angola", "Angola", "Anguilla", "Anguilla", "Anguilla", "Anguilla", 
"Anguilla", "Anguilla", "Anguilla", "Anguilla", "Anguilla", "Anguilla", 
"Anguilla", "Anguilla", "Anguilla", "Anguilla", "Antigua and Barbuda", 
"Antigua and Barbuda", "Antigua and Barbuda", "Antigua and Barbuda", 
"Antigua and Barbuda", "Antigua and Barbuda", "Antigua and Barbuda", 
"Antigua and Barbuda", "Antigua and Barbuda", "Antigua and Barbuda", 
"Antigua and Barbuda", "Antigua and Barbuda", "Antigua and Barbuda", 
"Antigua and Barbuda", "Antigua and Barbuda", "Antigua and Barbuda", 
"Antigua and Barbuda", "Antigua and Barbuda", "Antigua and Barbuda", 
"Antigua and Barbuda", "Antigua and Barbuda", "Antigua and Barbuda", 
"Antigua and Barbuda", "Argentina", "Argentina", "Argentina", 
"Argentina", "Argentina", "Argentina", "Argentina", "Argentina", 
"Argentina", "Argentina", "Argentina", "Argentina", "Argentina", 
"Argentina", "Argentina", "Argentina", "Argentina", "Argentina", 
"Argentina", "Argentina", "Argentina", "Argentina", "Argentina", 
"Argentina", "Argentina", "Argentina", "Argentina", "Argentina", 
"Argentina", "Argentina", "Argentina", "Argentina", "Argentina", 
"Argentina", "Armenia", "Armenia", "Armenia", "Armenia", "Armenia", 
"Armenia", "Armenia", "Armenia", "Armenia", "Armenia", "Armenia", 
"Armenia", "Armenia", "Armenia", "Armenia", "Armenia", "Armenia", 
"Armenia", "Armenia", "Armenia", "Armenia", "Armenia", "Armenia", 
"Armenia", "Armenia", "Armenia", "Armenia", "Armenia", "Armenia", 
"Armenia", "Armenia", "Armenia", "Armenia", "Armenia", "Armenia", 
"Aruba", "Aruba", "Aruba", "Aruba", "Aruba", "Aruba", "Aruba", 
"Aruba", "Aruba", "Aruba", "Aruba", "Aruba", "Aruba", "Aruba", 
"Aruba", "Aruba", "Aruba", "Aruba", "Aruba", "Aruba", "Aruba", 
"Aruba", "Aruba", "Aruba", "Aruba", "Aruba", "Aruba", "Aruba", 
"Aruba", "Aruba", "Australia", "Australia", "Australia", "Australia", 
"Australia", "Australia", "Australia", "Australia", "Australia", 
"Australia", "Australia", "Australia", "Australia", "Australia", 
"Australia", "Australia", "Australia", "Australia", "Australia", 
"Australia", "Australia", "Australia", "Australia", "Australia", 
"Australia", "Australia", "Australia", "Australia", "Australia", 
"Australia", "Australia", "Australia", "Australia", "Australia", 
"Austria", "Austria", "Austria", "Austria", "Austria", "Austria", 
"Austria", "Austria", "Austria", "Austria", "Austria", "Austria", 
"Austria", "Austria", "Austria", "Austria", "Austria", "Austria", 
"Austria", "Austria", "Austria", "Austria", "Austria", "Austria", 
"Austria", "Austria", "Austria", "Austria", "Austria", "Austria", 
"Austria", "Austria", "Austria", "Austria", "Austria", "Austria", 
"Azerbaijan", "Azerbaijan", "Azerbaijan", "Azerbaijan", "Azerbaijan", 
"Azerbaijan", "Azerbaijan", "Azerbaijan", "Azerbaijan", "Azerbaijan", 
"Azerbaijan", "Azerbaijan", "Azerbaijan", "Azerbaijan", "Azerbaijan", 
"Azerbaijan", "Azerbaijan", "Azerbaijan", "Azerbaijan", "Azerbaijan", 
"Azerbaijan", "Azerbaijan", "Azerbaijan", "Azerbaijan", "Azerbaijan", 
"Azerbaijan", "Azerbaijan", "Azerbaijan", "Azerbaijan", "Azerbaijan", 
"Azerbaijan", "Azerbaijan", "Azerbaijan", "Azerbaijan", "Azerbaijan", 
"Azerbaijan", "Bahamas", "Bahamas", "Bahamas", "Bahamas", "Bahamas", 
"Bahamas", "Bahamas", "Bahamas", "Bahamas", "Bahamas", "Bahamas", 
"Bahamas", "Bahamas", "Bahamas", "Bahamas", "Bahamas", "Bahamas", 
"Bahamas", "Bahamas", "Bahamas", "Bahamas", "Bahamas", "Bahamas", 
"Bahamas", "Bahamas", "Bahamas", "Bahamas", "Bahamas", "Bahamas", 
"Bahamas", "Bahamas", "Bahamas", "Bahamas", "Bahamas", "Bahamas", 
"Bahrain", "Bahrain", "Bahrain", "Bahrain", "Bahrain", "Bahrain", 
"Bahrain", "Bahrain", "Bahrain", "Bahrain", "Bahrain", "Bahrain", 
"Bahrain", "Bahrain", "Bahrain", "Bahrain", "Bahrain", "Bahrain", 
"Bahrain", "Bahrain", "Bahrain", "Bahrain", "Bahrain", "Bahrain", 
"Bahrain", "Bahrain", "Bahrain", "Bahrain", "Bahrain", "Bahrain", 
"Bangladesh", "Bangladesh", "Bangladesh", "Bangladesh", "Bangladesh", 
"Bangladesh", "Bangladesh", "Bangladesh", "Bangladesh", "Bangladesh", 
"Bangladesh", "Bangladesh", "Bangladesh", "Bangladesh", "Bangladesh", 
"Bangladesh", "Bangladesh", "Bangladesh", "Bangladesh", "Bangladesh", 
"Bangladesh", "Bangladesh", "Bangladesh", "Bangladesh", "Bangladesh", 
"Bangladesh", "Bangladesh", "Bangladesh", "Bangladesh", "Bangladesh", 
"Bangladesh", "Bangladesh", "Barbados", "Barbados", "Barbados", 
"Barbados", "Barbados", "Barbados", "Barbados", "Barbados", "Barbados", 
"Barbados", "Barbados", "Barbados", "Barbados", "Barbados", "Barbados", 
"Barbados", "Barbados", "Barbados", "Barbados", "Barbados", "Barbados", 
"Barbados", "Barbados", "Barbados", "Barbados", "Belarus", "Belarus", 
"Belarus", "Belarus", "Belarus", "Belarus", "Belarus", "Belarus", 
"Belarus", "Belarus", "Belarus", "Belarus", "Belarus", "Belarus", 
"Belarus", "Belarus", "Belarus", "Belarus", "Belarus", "Belarus", 
"Belarus", "Belarus", "Belarus", "Belarus", "Belarus", "Belarus", 
"Belarus", "Belarus", "Belarus", "Belarus", "Belarus", "Belarus", 
"Belarus", "Belarus", "Belarus", "Belarus", "Belgium", "Belgium", 
"Belgium", "Belgium", "Belgium", "Belgium", "Belgium", "Belgium", 
"Belgium", "Belgium", "Belgium", "Belgium", "Belgium", "Belgium", 
"Belgium", "Belgium", "Belgium", "Belgium", "Belgium", "Belgium", 
"Belgium", "Belgium", "Belgium", "Belgium", "Belgium", "Belgium", 
"Belgium", "Belgium", "Belgium", "Belgium", "Belgium", "Belgium", 
"Belgium", "Belgium", "Belgium", "Belgium", "Belize", "Belize", 
"Belize", "Belize", "Belize", "Belize", "Belize", "Belize", "Belize", 
"Belize", "Belize", "Belize", "Belize", "Belize", "Belize", "Belize", 
"Belize", "Belize", "Belize", "Belize", "Belize", "Belize", "Belize", 
"Belize", "Belize", "Belize", "Belize", "Belize", "Belize", "Belize", 
"Belize", "Belize", "Belize", "Benin", "Benin", "Benin", "Benin", 
"Benin", "Benin", "Benin", "Benin", "Benin", "Benin", "Benin", 
"Benin", "Benin", "Benin", "Benin", "Benin", "Benin", "Benin", 
"Benin", "Benin", "Benin", "Benin", "Benin", "Benin", "Benin", 
"Benin", "Benin", "Benin", "Benin", "Benin", "Benin", "Benin", 
"Benin", "Bermuda", "Bermuda", "Bermuda", "Bermuda", "Bermuda", 
"Bermuda", "Bermuda", "Bermuda", "Bhutan", "Bhutan", "Bhutan", 
"Bhutan", "Bhutan", "Bhutan", "Bhutan", "Bhutan", "Bhutan", "Bhutan", 
"Bhutan", "Bhutan", "Bhutan", "Bhutan", "Bhutan", "Bhutan", "Bolivia (Plurin. State of)", 
"Bolivia (Plurin. State of)", "Bolivia (Plurin. State of)", "Bolivia (Plurin. State of)", 
"Bolivia (Plurin. State of)", "Bolivia (Plurin. State of)", "Bolivia (Plurin. State of)", 
"Bolivia (Plurin. State of)", "Bolivia (Plurin. State of)", "Bolivia (Plurin. State of)", 
"Bolivia (Plurin. State of)", "Bolivia (Plurin. State of)", "Bolivia (Plurin. State of)", 
"Bolivia (Plurin. State of)", "Bolivia (Plurin. State of)", "Bolivia (Plurin. State of)", 
"Bolivia (Plurin. State of)", "Bolivia (Plurin. State of)", "Bolivia (Plurin. State of)", 
"Bolivia (Plurin. State of)", "Bolivia (Plurin. State of)", "Bolivia (Plurin. State of)", 
"Bolivia (Plurin. State of)", "Bolivia (Plurin. State of)", "Bolivia (Plurin. State of)", 
"Bolivia (Plurin. State of)", "Bolivia (Plurin. State of)", "Bolivia (Plurin. State of)", 
"Bolivia (Plurin. State of)", "Bolivia (Plurin. State of)", "Bolivia (Plurin. State of)", 
"Bolivia (Plurin. State of)", "Bolivia (Plurin. State of)", "Bolivia (Plurin. State of)", 
"Bolivia (Plurin. State of)", "Bonaire, St. Eustatius & Saba", 
"Bonaire, St. Eustatius & Saba", "Bonaire, St. Eustatius & Saba", 
"Bonaire, St. Eustatius & Saba", "Bonaire, St. Eustatius & Saba", 
"Bonaire, St. Eustatius & Saba", "Bonaire, St. Eustatius & Saba", 
"Bonaire, St. Eustatius & Saba", "Bonaire, St. Eustatius & Saba", 
"Bonaire, St. Eustatius & Saba", "Bosnia and Herzegovina", "Bosnia and Herzegovina", 
"Bosnia and Herzegovina", "Bosnia and Herzegovina", "Bosnia and Herzegovina", 
"Bosnia and Herzegovina", "Bosnia and Herzegovina", "Bosnia and Herzegovina", 
"Bosnia and Herzegovina", "Bosnia and Herzegovina", "Bosnia and Herzegovina", 
"Bosnia and Herzegovina", "Bosnia and Herzegovina", "Bosnia and Herzegovina", 
"Bosnia and Herzegovina", "Bosnia and Herzegovina", "Bosnia and Herzegovina", 
"Bosnia and Herzegovina", "Bosnia and Herzegovina", "Bosnia and Herzegovina", 
"Bosnia and Herzegovina", "Bosnia and Herzegovina", "Bosnia and Herzegovina", 
"Bosnia and Herzegovina", "Bosnia and Herzegovina", "Bosnia and Herzegovina", 
"Bosnia and Herzegovina", "Bosnia and Herzegovina", "Bosnia and Herzegovina", 
"Bosnia and Herzegovina", "Bosnia and Herzegovina", "Bosnia and Herzegovina", 
"Bosnia and Herzegovina", "Bosnia and Herzegovina", "Bosnia and Herzegovina", 
"Bosnia and Herzegovina", "Botswana", "Botswana", "Botswana", 
"Botswana", "Botswana", "Botswana", "Botswana", "Botswana", "Botswana", 
"Botswana", "Botswana", "Botswana", "Botswana", "Botswana", "Botswana", 
"Botswana", "Botswana", "Botswana", "Botswana", "Botswana", "Botswana", 
"Botswana", "Botswana", "Botswana", "Botswana", "Botswana", "Botswana", 
"Botswana", "Botswana", "Botswana", "Botswana", "Botswana", "Botswana", 
"Botswana", "Botswana", "Brazil", "Brazil", "Brazil", "Brazil", 
"Brazil", "Brazil", "Brazil", "Brazil", "Brazil", "Brazil", "Brazil", 
"Brazil", "Brazil", "Brazil", "Brazil", "Brazil", "Brazil", "Brazil", 
"Brazil", "Brazil", "Brazil", "Brazil", "Brazil", "Brazil", "Brazil", 
"Brazil", "Brazil", "Brazil", "Brazil", "Brazil", "Brazil", "Brazil", 
"Brazil", "Brazil", "Brazil", "Brazil", "British Virgin Islands", 
"British Virgin Islands", "British Virgin Islands", "British Virgin Islands", 
"British Virgin Islands", "British Virgin Islands", "British Virgin Islands", 
"British Virgin Islands", "British Virgin Islands", "British Virgin Islands", 
"British Virgin Islands", "British Virgin Islands", "British Virgin Islands", 
"British Virgin Islands", "British Virgin Islands", "British Virgin Islands", 
"British Virgin Islands", "British Virgin Islands", "Brunei Darussalam", 
"Brunei Darussalam", "Brunei Darussalam", "Brunei Darussalam", 
"Brunei Darussalam", "Brunei Darussalam", "Brunei Darussalam", 
"Brunei Darussalam", "Brunei Darussalam", "Brunei Darussalam", 
"Brunei Darussalam", "Brunei Darussalam", "Brunei Darussalam", 
"Brunei Darussalam", "Brunei Darussalam", "Brunei Darussalam", 
"Brunei Darussalam", "Brunei Darussalam", "Brunei Darussalam", 
"Brunei Darussalam", "Brunei Darussalam", "Brunei Darussalam", 
"Brunei Darussalam", "Brunei Darussalam", "Bulgaria", "Bulgaria", 
"Bulgaria", "Bulgaria", "Bulgaria", "Bulgaria", "Bulgaria", "Bulgaria", 
"Bulgaria", "Bulgaria", "Bulgaria", "Bulgaria", "Bulgaria", "Bulgaria", 
"Bulgaria", "Bulgaria", "Bulgaria", "Bulgaria", "Bulgaria", "Bulgaria", 
"Bulgaria", "Bulgaria", "Bulgaria", "Bulgaria", "Bulgaria", "Bulgaria", 
"Bulgaria", "Bulgaria", "Bulgaria", "Bulgaria", "Bulgaria", "Bulgaria", 
"Bulgaria", "Bulgaria", "Burkina Faso", "Burkina Faso", "Burkina Faso", 
"Burkina Faso", "Burkina Faso", "Burkina Faso", "Burkina Faso", 
"Burkina Faso", "Burkina Faso", "Burkina Faso", "Burkina Faso", 
"Burkina Faso", "Burkina Faso", "Burkina Faso", "Burkina Faso", 
"Burkina Faso", "Burkina Faso", "Burkina Faso", "Burkina Faso", 
"Burkina Faso", "Burkina Faso", "Burkina Faso", "Burkina Faso", 
"Burkina Faso", "Burkina Faso", "Burkina Faso", "Burkina Faso", 
"Burkina Faso", "Burkina Faso", "Burkina Faso", "Burkina Faso", 
"Burkina Faso", "Burkina Faso", "Burkina Faso", "Burkina Faso", 
"Burundi", "Burundi", "Burundi", "Burundi", "Burundi", "Burundi", 
"Burundi", "Burundi", "Burundi", "Burundi", "Burundi", "Burundi", 
"Burundi", "Burundi", "Burundi", "Burundi", "Burundi", "Burundi", 
"Burundi", "Burundi", "Burundi", "Burundi", "Burundi", "Burundi", 
"Burundi", "Burundi", "Burundi", "Burundi", "Burundi", "Burundi", 
"Burundi", "Burundi", "Burundi", "Burundi", "Burundi", "Burundi", 
"Cabo Verde", "Cabo Verde", "Cabo Verde", "Cabo Verde", "Cabo Verde", 
"Cabo Verde", "Cabo Verde", "Cabo Verde", "Cabo Verde", "Cabo Verde", 
"Cabo Verde", "Cabo Verde", "Cabo Verde", "Cabo Verde", "Cabo Verde", 
"Cabo Verde", "Cabo Verde", "Cabo Verde", "Cabo Verde", "Cabo Verde", 
"Cabo Verde", "Cabo Verde", "Cabo Verde", "Cabo Verde", "Cambodia", 
"Cambodia", "Cambodia", "Cambodia", "Cambodia", "Cambodia", "Cambodia", 
"Cambodia", "Cambodia", "Cambodia", "Cambodia", "Cambodia", "Cambodia", 
"Cambodia", "Cambodia", "Cambodia", "Cambodia", "Cambodia", "Cambodia", 
"Cambodia", "Cambodia", "Cambodia", "Cambodia", "Cambodia", "Cambodia", 
"Cambodia", "Cambodia", "Cambodia", "Cambodia", "Cambodia", "Cambodia", 
"Cambodia", "Cambodia", "Cambodia", "Cameroon", "Cameroon", "Cameroon", 
"Cameroon", "Cameroon", "Cameroon", "Cameroon", "Cameroon", "Cameroon", 
"Cameroon", "Cameroon", "Cameroon", "Cameroon", "Cameroon", "Cameroon", 
"Cameroon", "Cameroon", "Cameroon", "Cameroon", "Cameroon", "Cameroon", 
"Cameroon", "Cameroon", "Cameroon", "Cameroon", "Cameroon", "Cameroon", 
"Cameroon", "Cameroon", "Cameroon", "Cameroon", "Cameroon", "Cameroon", 
"Cameroon", "Cameroon", "Cameroon", "Canada", "Canada", "Canada", 
"Canada", "Canada", "Canada", "Canada", "Canada", "Canada", "Canada", 
"Canada", "Canada", "Canada", "Canada", "Canada", "Canada", "Canada", 
"Canada", "Canada", "Canada", "Canada", "Canada", "Canada", "Canada", 
"Canada", "Canada", "Canada", "Canada", "Canada", "Canada", "Canada", 
"Canada", "Canada", "Canada", "Canada", "Cayman Islands", "Cayman Islands", 
"Cayman Islands", "Cayman Islands", "Cayman Islands", "Cayman Islands", 
"Cayman Islands", "Cayman Islands", "Cayman Islands", "Cayman Islands", 
"Cayman Islands", "Cayman Islands", "Cayman Islands", "Cayman Islands", 
"Cayman Islands", "Cayman Islands", "Cayman Islands", "Cayman Islands", 
"Cayman Islands", "Cayman Islands", "Cayman Islands", "Cayman Islands", 
"Cayman Islands", "Central African Republic", "Central African Republic", 
"Central African Republic", "Central African Republic", "Central African Republic", 
"Central African Republic", "Central African Republic", "Central African Republic", 
"Central African Republic", "Central African Republic", "Central African Republic", 
"Central African Republic", "Central African Republic", "Central African Republic", 
"Central African Republic", "Central African Republic", "Central African Republic", 
"Central African Republic", "Central African Republic", "Central African Republic", 
"Central African Republic", "Central African Republic", "Central African Republic", 
"Central African Republic", "Central African Republic", "Central African Republic", 
"Central African Republic", "Central African Republic", "Central African Republic", 
"Central African Republic", "Central African Republic", "Central African Republic", 
"Central African Republic", "Central African Republic", "Central African Republic", 
"Central African Republic", "Chad", "Chad", "Chad", "Chad", "Chad", 
"Chad", "Chad", "Chad", "Chad", "Chad", "Chad", "Chad", "Chad", 
"Chad", "Chad", "Chad", "Chad", "Chad", "Chad", "Chad", "Chad", 
"Chad", "Chad", "Chad", "Chad", "Chad", "Chad", "Chad", "Chad", 
"Chad", "Chad", "Chad", "Chad", "Chad", "Chad", "Chile", "Chile", 
"Chile", "Chile", "Chile", "Chile", "Chile", "Chile", "Chile", 
"Chile", "Chile", "Chile", "Chile", "Chile", "Chile", "Chile", 
"Chile", "Chile", "Chile", "Chile", "Chile", "Chile", "Chile", 
"Chile", "Chile", "Chile", "Chile", "Chile", "Chile", "Chile", 
"Chile", "Chile", "Chile", "China", "China", "China", "China", 
"China", "China", "China", "China", "China", "China", "China", 
"China", "China", "China", "China", "China", "China", "China", 
"China", "China", "China", "China", "China", "China", "China", 
"China", "China", "China", "China", "China", "China", "China", 
"China, Hong Kong SAR", "China, Hong Kong SAR", "China, Hong Kong SAR", 
"China, Hong Kong SAR", "China, Hong Kong SAR", "China, Hong Kong SAR", 
"China, Hong Kong SAR", "China, Hong Kong SAR", "China, Hong Kong SAR", 
"China, Hong Kong SAR", "China, Hong Kong SAR", "China, Hong Kong SAR", 
"China, Hong Kong SAR", "China, Hong Kong SAR", "China, Hong Kong SAR", 
"China, Hong Kong SAR", "China, Hong Kong SAR", "China, Hong Kong SAR", 
"China, Hong Kong SAR", "China, Hong Kong SAR", "China, Hong Kong SAR", 
"China, Hong Kong SAR", "China, Hong Kong SAR", "China, Hong Kong SAR", 
"China, Hong Kong SAR", "China, Hong Kong SAR", "China, Hong Kong SAR", 
"China, Hong Kong SAR", "China, Hong Kong SAR", "China, Hong Kong SAR", 
"China, Hong Kong SAR", "China, Hong Kong SAR", "China, Hong Kong SAR", 
"China, Hong Kong SAR", "China, Hong Kong SAR", "China, Hong Kong SAR", 
"China, Hong Kong SAR", "China, Hong Kong SAR", "China, Macao SAR", 
"China, Macao SAR", "China, Macao SAR", "China, Macao SAR", "China, Macao SAR", 
"China, Macao SAR", "China, Macao SAR", "China, Macao SAR", "China, Macao SAR", 

"Republic of Korea", "Republic of Korea", "Republic of Korea", 
"Republic of Korea", "Republic of Korea", "Republic of Moldova", 
"Republic of Moldova", "Republic of Moldova", "Republic of Moldova", 
"Republic of Moldova", "Republic of Moldova", "Republic of Moldova", 
"Republic of Moldova", "Republic of Moldova", "Republic of Moldova", 
"Republic of Moldova", "Republic of Moldova", "Republic of Moldova", 
"Republic of Moldova", "Republic of Moldova", "Republic of Moldova", 
"Republic of Moldova", "Republic of Moldova", "Republic of Moldova", 
"Republic of Moldova", "Republic of Moldova", "Republic of Moldova", 
"Republic of Moldova", "Republic of Moldova", "Republic of Moldova", 
"Republic of Moldova", "Republic of Moldova", "Republic of Moldova", 
"Republic of Moldova", "Republic of Moldova", "Republic of Moldova", 
"Republic of Moldova", "Republic of Moldova", "Republic of Moldova", 
"Republic of Moldova", "Republic of Moldova", "R\xe9union", "R\xe9union", 
"R\xe9union", "R\xe9union", "R\xe9union", "R\xe9union", "R\xe9union", 
"R\xe9union", "R\xe9union", "R\xe9union", "R\xe9union", "R\xe9union", 
"R\xe9union", "R\xe9union", "R\xe9union", "R\xe9union", "Romania", 
"Romania", "Romania", "Romania", "Romania", "Romania", "Romania", 
"Romania", "Romania", "Romania", "Romania", "Romania", "Romania", 
"Romania", "Romania", "Romania", "Romania", "Romania", "Romania", 
"Romania", "Romania", "Romania", "Romania", "Romania", "Romania", 
"Romania", "Romania", "Romania", "Romania", "Romania", "Romania", 
"Romania", "Romania", "Romania", "Romania", "Romania", "Russian Federation", 
"Russian Federation", "Russian Federation", "Russian Federation", 
"Russian Federation", "Russian Federation", "Russian Federation", 
"Russian Federation", "Russian Federation", "Russian Federation", 
"Russian Federation", "Russian Federation", "Russian Federation", 
"Russian Federation", "Russian Federation", "Russian Federation", 
"Russian Federation", "Russian Federation", "Russian Federation", 
"Russian Federation", "Russian Federation", "Russian Federation", 
"Russian Federation", "Russian Federation", "Russian Federation", 
"Russian Federation", "Russian Federation", "Russian Federation", 
"Russian Federation", "Russian Federation", "Russian Federation", 
"Russian Federation", "Russian Federation", "Russian Federation", 
"Russian Federation", "Russian Federation", "Rwanda", "Rwanda", 
"Rwanda", "Rwanda", "Rwanda", "Rwanda", "Rwanda", "Rwanda", "Rwanda", 
"Rwanda", "Rwanda", "Rwanda", "Rwanda", "Rwanda", "Rwanda", "Rwanda", 
"Rwanda", "Rwanda", "Rwanda", "Rwanda", "Rwanda", "Rwanda", "Rwanda", 
"Rwanda", "Rwanda", "Rwanda", "Rwanda", "Rwanda", "Rwanda", "Rwanda", 
"Rwanda", "Rwanda", "Rwanda", "Rwanda", "Rwanda", "Rwanda", "Saint Helena", 
"Saint Helena", "Saint Helena", "Saint Helena", "Saint Helena", 
"Saint Helena", "Saint Helena", "Saint Helena", "Saint Kitts and Nevis", 
"Saint Kitts and Nevis", "Saint Kitts and Nevis", "Saint Kitts and Nevis", 
"Saint Kitts and Nevis", "Saint Kitts and Nevis", "Saint Kitts and Nevis", 
"Saint Kitts and Nevis", "Saint Kitts and Nevis", "Saint Kitts and Nevis", 
"Saint Kitts and Nevis", "Saint Kitts and Nevis", "Saint Kitts and Nevis", 
"Saint Kitts and Nevis", "Saint Lucia", "Saint Lucia", "Saint Lucia", 
"Saint Lucia", "Saint Lucia", "Saint Lucia", "Saint Lucia", "Saint Lucia", 
"Saint Lucia", "Saint Lucia", "Saint Lucia", "Saint Lucia", "Saint Lucia", 
"Saint Lucia", "Saint Lucia", "Saint Lucia", "Saint Lucia", "Saint Lucia", 
"Saint Lucia", "Saint Lucia", "Saint Lucia", "Saint Lucia", "Saint Lucia", 
"Saint Lucia", "Saint Lucia", "Saint Lucia", "Saint Pierre and Miquelon", 
"Saint Pierre and Miquelon", "Saint Pierre and Miquelon", "Saint Pierre and Miquelon", 
"Saint Pierre and Miquelon", "Saint Pierre and Miquelon", "Saint Pierre and Miquelon", 
"Saint Pierre and Miquelon", "Saint Vincent & Grenadines", "Saint Vincent & Grenadines", 
"Saint Vincent & Grenadines", "Saint Vincent & Grenadines", "Saint Vincent & Grenadines", 
"Saint Vincent & Grenadines", "Saint Vincent & Grenadines", "Saint Vincent & Grenadines", 
"Saint Vincent & Grenadines", "Saint Vincent & Grenadines", "Saint Vincent & Grenadines", 
"Saint Vincent & Grenadines", "Saint Vincent & Grenadines", "Saint Vincent & Grenadines", 
"Saint Vincent & Grenadines", "Saint Vincent & Grenadines", "Saint Vincent & Grenadines", 
"Saint Vincent & Grenadines", "Saint Vincent & Grenadines", "Saint Vincent & Grenadines", 
"Samoa", "Samoa", "Samoa", "Samoa", "Samoa", "Samoa", "Samoa", 
"Samoa", "Samoa", "Samoa", "Samoa", "Samoa", "Samoa", "Samoa", 
"Samoa", "Samoa", "Samoa", "Samoa", "Samoa", "Samoa", "San Marino", 
"San Marino", "San Marino", "San Marino", "San Marino", "San Marino", 
"San Marino", "San Marino", "Sao Tome and Principe", "Sao Tome and Principe", 
"Sao Tome and Principe", "Sao Tome and Principe", "Sao Tome and Principe", 
"Sao Tome and Principe", "Sao Tome and Principe", "Sao Tome and Principe", 
"Sao Tome and Principe", "Sao Tome and Principe", "Sao Tome and Principe", 
"Sao Tome and Principe", "Sao Tome and Principe", "Sao Tome and Principe", 
"Sao Tome and Principe", "Sao Tome and Principe", "Saudi Arabia", 
"Saudi Arabia", "Saudi Arabia", "Saudi Arabia", "Saudi Arabia", 
"Saudi Arabia", "Saudi Arabia", "Saudi Arabia", "Saudi Arabia", 
"Saudi Arabia", "Saudi Arabia", "Saudi Arabia", "Saudi Arabia", 
"Saudi Arabia", "Saudi Arabia", "Saudi Arabia", "Saudi Arabia", 
"Saudi Arabia", "Saudi Arabia", "Saudi Arabia", "Saudi Arabia", 
"Saudi Arabia", "Saudi Arabia", "Saudi Arabia", "Saudi Arabia", 
"Saudi Arabia", "Saudi Arabia", "Saudi Arabia", "Saudi Arabia", 
"Saudi Arabia", "Saudi Arabia", "Saudi Arabia", "Saudi Arabia", 
"Saudi Arabia", "Saudi Arabia", "Saudi Arabia", "Senegal", "Senegal", 
"Senegal", "Senegal", "Senegal", "Senegal", "Senegal", "Senegal", 
"Senegal", "Senegal", "Senegal", "Senegal", "Senegal", "Senegal", 
"Senegal", "Senegal", "Senegal", "Senegal", "Senegal", "Senegal", 
"Senegal", "Senegal", "Senegal", "Senegal", "Senegal", "Senegal", 
"Senegal", "Senegal", "Senegal", "Senegal", "Senegal", "Senegal", 
"Senegal", "Senegal", "Senegal", "Senegal", "Senegal", "Serbia", 
"Serbia", "Serbia", "Serbia", "Serbia", "Serbia", "Serbia", "Serbia", 
"Serbia", "Serbia", "Serbia", "Serbia", "Serbia", "Serbia", "Serbia", 
"Serbia", "Serbia", "Serbia", "Serbia", "Serbia", "Serbia", "Serbia", 
"Serbia", "Serbia", "Serbia", "Serbia", "Serbia", "Serbia", "Serbia", 
"Serbia", "Serbia", "Serbia", "Serbia", "Serbia", "Serbia", "Serbia", 
"Seychelles", "Seychelles", "Seychelles", "Seychelles", "Seychelles", 
"Seychelles", "Seychelles", "Seychelles", "Seychelles", "Seychelles", 
"Seychelles", "Seychelles", "Seychelles", "Seychelles", "Seychelles", 
"Seychelles", "Seychelles", "Seychelles", "Sierra Leone", "Sierra Leone", 
"Sierra Leone", "Sierra Leone", "Sierra Leone", "Sierra Leone", 
"Sierra Leone", "Sierra Leone", "Sierra Leone", "Sierra Leone", 
"Sierra Leone", "Sierra Leone", "Sierra Leone", "Sierra Leone", 
"Sierra Leone", "Sierra Leone", "Sierra Leone", "Sierra Leone", 
"Sierra Leone", "Sierra Leone", "Sierra Leone", "Sierra Leone", 
"Sierra Leone", "Sierra Leone", "Sierra Leone", "Sierra Leone", 
"Sierra Leone", "Sierra Leone", "Sierra Leone", "Sierra Leone", 
"Sierra Leone", "Sierra Leone", "Sierra Leone", "Sierra Leone", 
"Sierra Leone", "Singapore", "Singapore", "Singapore", "Singapore", 
"Singapore", "Singapore", "Singapore", "Singapore", "Singapore", 
"Singapore", "Singapore", "Singapore", "Singapore", "Singapore", 
"Singapore", "Singapore", "Singapore", "Singapore", "Singapore", 
"Singapore", "Singapore", "Singapore", "Singapore", "Singapore", 
"Singapore", "Singapore", "Singapore", "Singapore", "Sint Maarten (Dutch part)", 
"Sint Maarten (Dutch part)", "Sint Maarten (Dutch part)", "Sint Maarten (Dutch part)", 
"Sint Maarten (Dutch part)", "Sint Maarten (Dutch part)", "Sint Maarten (Dutch part)", 
"Sint Maarten (Dutch part)", "Sint Maarten (Dutch part)", "Sint Maarten (Dutch part)", 
"Sint Maarten (Dutch part)", "Sint Maarten (Dutch part)", "Sint Maarten (Dutch part)", 
"Sint Maarten (Dutch part)", "Sint Maarten (Dutch part)", "Sint Maarten (Dutch part)", 
"Sint Maarten (Dutch part)", "Sint Maarten (Dutch part)", "Sint Maarten (Dutch part)", 
"Sint Maarten (Dutch part)", "Slovakia", "Slovakia", "Slovakia", 
"Slovakia", "Slovakia", "Slovakia", "Slovakia", "Slovakia", "Slovakia", 
"Slovakia", "Slovakia", "Slovakia", "Slovakia", "Slovakia", "Slovakia", 
"Slovakia", "Slovakia", "Slovakia", "Slovakia", "Slovakia", "Slovakia", 
"Slovakia", "Slovakia", "Slovakia", "Slovakia", "Slovakia", "Slovakia", 
"Slovakia", "Slovakia", "Slovakia", "Slovakia", "Slovakia", "Slovakia", 
"Slovakia", "Slovakia", "Slovenia", "Slovenia", "Slovenia", "Slovenia", 
"Slovenia", "Slovenia", "Slovenia", "Slovenia", "Slovenia", "Slovenia", 
"Slovenia", "Slovenia", "Slovenia", "Slovenia", "Slovenia", "Slovenia", 
"Slovenia", "Slovenia", "Slovenia", "Slovenia", "Slovenia", "Slovenia", 
"Slovenia", "Slovenia", "Slovenia", "Slovenia", "Slovenia", "Slovenia", 
"Slovenia", "Slovenia", "Slovenia", "Slovenia", "Slovenia", "Slovenia", 
"Slovenia", "Slovenia", "Slovenia", "Slovenia", "Slovenia", "Solomon Islands", 
"Solomon Islands", "Solomon Islands", "Solomon Islands", "Solomon Islands", 
"Solomon Islands", "Solomon Islands", "Solomon Islands", "Solomon Islands", 
"Solomon Islands", "Solomon Islands", "Solomon Islands", "Solomon Islands", 
"Solomon Islands", "Solomon Islands", "Solomon Islands", "Solomon Islands", 
"Solomon Islands", "Solomon Islands", "Solomon Islands", "Solomon Islands", 
"Solomon Islands", "Somalia", "Somalia", "Somalia", "Somalia", 
"Somalia", "Somalia", "Somalia", "Somalia", "Somalia", "Somalia", 
"Somalia", "Somalia", "Somalia", "Somalia", "Somalia", "Somalia", 
"Somalia", "Somalia", "Somalia", "Somalia", "Somalia", "Somalia", 
"Somalia", "Somalia", "Somalia", "Somalia", "Somalia", "Somalia", 
"Somalia", "Somalia", "Somalia", "Somalia", "Somalia", "Somalia", 
"Somalia", "Somalia", "South Africa", "South Africa", "South Africa", 
"South Africa", "South Africa", "South Africa", "South Africa", 
"South Africa", "South Africa", "South Africa", "South Africa", 
"South Africa", "South Africa", "South Africa", "South Africa", 
"South Africa", "South Africa", "South Africa", "South Africa", 
"South Africa", "South Africa", "South Africa", "South Africa", 
"South Africa", "South Africa", "South Africa", "South Africa", 
"South Africa", "South Africa", "South Africa", "South Africa", 
"South Africa", "South Africa", "South Sudan", "South Sudan", 
"South Sudan", "South Sudan", "South Sudan", "South Sudan", "South Sudan", 
"South Sudan", "South Sudan", "South Sudan", "South Sudan", "South Sudan", 
"South Sudan", "South Sudan", "South Sudan", "South Sudan", "South Sudan", 
"South Sudan", "South Sudan", "South Sudan", "South Sudan", "South Sudan", 
"South Sudan", "South Sudan", "Spain", "Spain", "Spain", "Spain", 
"Spain", "Spain", "Spain", "Spain", "Spain", "Spain", "Spain", 
"Spain", "Spain", "Spain", "Spain", "Spain", "Spain", "Spain", 
"Spain", "Spain", "Spain", "Spain", "Spain", "Spain", "Spain", 
"Spain", "Spain", "Spain", "Spain", "Spain", "Spain", "Spain", 
"Spain", "Spain", "Spain", "Sri Lanka", "Sri Lanka", "Sri Lanka", 
"Sri Lanka", "Sri Lanka", "Sri Lanka", "Sri Lanka", "Sri Lanka", 
"Sri Lanka", "Sri Lanka", "Sri Lanka", "Sri Lanka", "Sri Lanka", 
"Sri Lanka", "Sri Lanka", "Sri Lanka", "Sri Lanka", "Sri Lanka", 
"Sri Lanka", "Sri Lanka", "Sri Lanka", "Sri Lanka", "Sri Lanka", 
"Sri Lanka", "Sri Lanka", "Sri Lanka", "Sri Lanka", "Sri Lanka", 
"Sri Lanka", "Sri Lanka", "Sri Lanka", "Sri Lanka", "Sri Lanka", 
"Sri Lanka", "Sri Lanka", "Sri Lanka", "State of Palestine", 
"State of Palestine", "State of Palestine", "State of Palestine", 
"State of Palestine", "State of Palestine", "State of Palestine", 
"State of Palestine", "State of Palestine", "State of Palestine", 
"State of Palestine", "State of Palestine", "State of Palestine", 
"State of Palestine", "State of Palestine", "State of Palestine", 
"State of Palestine", "State of Palestine", "Sudan", "Sudan", 
"Sudan", "Sudan", "Sudan", "Sudan", "Sudan", "Sudan", "Sudan", 
"Sudan", "Sudan", "Sudan", "Sudan", "Sudan", "Sudan", "Sudan", 
"Sudan", "Sudan", "Sudan", "Sudan", "Sudan", "Sudan", "Sudan", 
"Sudan", "Sudan", "Sudan", "Sudan", "Sudan", "Sudan", "Sudan", 
"Sudan", "Sudan", "Sudan", "Sudan", "Sudan", "Sudan", "Suriname", 
"Suriname", "Suriname", "Suriname", "Suriname", "Suriname", "Suriname", 
"Suriname", "Suriname", "Suriname", "Suriname", "Suriname", "Suriname", 
"Suriname", "Suriname", "Suriname", "Suriname", "Suriname", "Suriname", 
"Suriname", "Suriname", "Suriname", "Suriname", "Suriname", "Suriname", 
"Suriname", "Suriname", "Suriname", "Suriname", "Suriname", "Suriname", 
"Sweden", "Sweden", "Sweden", "Sweden", "Sweden", "Sweden", "Sweden", 
"Sweden", "Sweden", "Sweden", "Sweden", "Sweden", "Sweden", "Sweden", 
"Sweden", "Sweden", "Sweden", "Sweden", "Sweden", "Sweden", "Sweden", 
"Sweden", "Sweden", "Sweden", "Sweden", "Sweden", "Sweden", "Sweden", 
"Sweden", "Sweden", "Sweden", "Sweden", "Sweden", "Sweden", "Sweden", 
"Sweden", "Switzerland", "Switzerland", "Switzerland", "Switzerland", 
"Switzerland", "Switzerland", "Switzerland", "Switzerland", "Switzerland", 
"Switzerland", "Switzerland", "Switzerland", "Switzerland", "Switzerland", 
"Switzerland", "Switzerland", "Switzerland", "Switzerland", "Switzerland", 
"Switzerland", "Switzerland", "Switzerland", "Switzerland", "Switzerland", 
"Switzerland", "Switzerland", "Switzerland", "Switzerland", "Switzerland", 
"Switzerland", "Switzerland", "Switzerland", "Switzerland", "Switzerland", 
"Switzerland", "Syrian Arab Republic", "Syrian Arab Republic", 
"Syrian Arab Republic", "Syrian Arab Republic", "Syrian Arab Republic", 
"Syrian Arab Republic", "Syrian Arab Republic", "Syrian Arab Republic", 
"Syrian Arab Republic", "Syrian Arab Republic", "Syrian Arab Republic", 
"Syrian Arab Republic", "Syrian Arab Republic", "Syrian Arab Republic", 
"Syrian Arab Republic", "Syrian Arab Republic", "Syrian Arab Republic", 
"Syrian Arab Republic", "Syrian Arab Republic", "Syrian Arab Republic", 
"Syrian Arab Republic", "Syrian Arab Republic", "Syrian Arab Republic", 
"Syrian Arab Republic", "Syrian Arab Republic", "Syrian Arab Republic", 
"Syrian Arab Republic", "Syrian Arab Republic", "Syrian Arab Republic", 
"Syrian Arab Republic", "Syrian Arab Republic", "Syrian Arab Republic", 
"Syrian Arab Republic", "Syrian Arab Republic", "Syrian Arab Republic", 
"Syrian Arab Republic", "Tajikistan", "Tajikistan", "Tajikistan", 
"Tajikistan", "Tajikistan", "Tajikistan", "Tajikistan", "Tajikistan", 
"Tajikistan", "Tajikistan", "Tajikistan", "Tajikistan", "Tajikistan", 
"Tajikistan", "Tajikistan", "Tajikistan", "Tajikistan", "Tajikistan", 
"Tajikistan", "Tajikistan", "Tajikistan", "Tajikistan", "Tajikistan", 
"Tajikistan", "Tajikistan", "Tajikistan", "Tajikistan", "Tajikistan", 
"Tajikistan", "Tajikistan", "Tajikistan", "Tajikistan", "Tajikistan", 
"Tajikistan", "Tajikistan", "Tajikistan", "Thailand", "Thailand", 
"Thailand", "Thailand", "Thailand", "Thailand", "Thailand", "Thailand", 
"Thailand", "Thailand", "Thailand", "Thailand", "Thailand", "Thailand", 
"Thailand", "Thailand", "Thailand", "Thailand", "Thailand", "Thailand", 
"Thailand", "Thailand", "Thailand", "Thailand", "Thailand", "Thailand", 
"Thailand", "Thailand", "Thailand", "Thailand", "Thailand", "Thailand", 
"Thailand", "Thailand", "Thailand", "Thailand", "Timor-Leste", 
"Timor-Leste", "Timor-Leste", "Timor-Leste", "Timor-Leste", "Timor-Leste", 
"Timor-Leste", "Timor-Leste", "Timor-Leste", "Timor-Leste", "Timor-Leste", 
"Timor-Leste", "Timor-Leste", "Timor-Leste", "Timor-Leste", "Timor-Leste", 
"Timor-Leste", "Timor-Leste", "Timor-Leste", "Timor-Leste", "Timor-Leste", 
"Timor-Leste", "Timor-Leste", "Timor-Leste", "Timor-Leste", "Timor-Leste", 
"Togo", "Togo", "Togo", "Togo", "Togo", "Togo", "Togo", "Togo", 
"Togo", "Togo", "Togo", "Togo", "Togo", "Togo", "Togo", "Togo", 
"Togo", "Togo", "Togo", "Togo", "Togo", "Togo", "Togo", "Togo", 
"Togo", "Togo", "Togo", "Togo", "Togo", "Togo", "Togo", "Togo", 
"Togo", "Togo", "Togo", "Togo", "Togo", "Tokelau", "Tokelau", 
"Tokelau", "Tokelau", "Tokelau", "Tokelau", "Tokelau", "Tokelau", 
"Tonga", "Tonga", "Tonga", "Tonga", "Tonga", "Tonga", "Tonga", 
"Tonga", "Tonga", "Tonga", "Tonga", "Tonga", "Tonga", "Tonga", 
"Tonga", "Tonga", "Tonga", "Tonga", "Tonga", "Tonga", "Trinidad and Tobago", 
"Trinidad and Tobago", "Trinidad and Tobago", "Trinidad and Tobago", 
"Trinidad and Tobago", "Trinidad and Tobago", "Trinidad and Tobago", 
"Trinidad and Tobago", "Trinidad and Tobago", "Trinidad and Tobago", 
"Trinidad and Tobago", "Trinidad and Tobago", "Trinidad and Tobago", 
"Trinidad and Tobago", "Trinidad and Tobago", "Trinidad and Tobago", 
"Trinidad and Tobago", "Trinidad and Tobago", "Trinidad and Tobago", 
"Trinidad and Tobago", "Trinidad and Tobago", "Trinidad and Tobago", 
"Trinidad and Tobago", "Trinidad and Tobago", "Trinidad and Tobago", 
"Trinidad and Tobago", "Trinidad and Tobago", "Trinidad and Tobago", 
"Trinidad and Tobago", "Trinidad and Tobago", "Tunisia", "Tunisia", 
"Tunisia", "Tunisia", "Tunisia", "Tunisia", "Tunisia", "Tunisia", 
"Tunisia", "Tunisia", "Tunisia", "Tunisia", "Tunisia", "Tunisia", 
"Tunisia", "Tunisia", "Tunisia", "Tunisia", "Tunisia", "Tunisia", 
"Tunisia", "Tunisia", "Tunisia", "Tunisia", "Tunisia", "Tunisia", 
"Tunisia", "Tunisia", "Tunisia", "Tunisia", "Tunisia", "Tunisia", 
"Tunisia", "Tunisia", "Tunisia", "T\xfcrkiye", "T\xfcrkiye", 
"T\xfcrkiye", "T\xfcrkiye", "T\xfcrkiye", "T\xfcrkiye", "T\xfcrkiye", 
"T\xfcrkiye", "T\xfcrkiye", "T\xfcrkiye", "T\xfcrkiye", "T\xfcrkiye", 
"T\xfcrkiye", "T\xfcrkiye", "T\xfcrkiye", "T\xfcrkiye", "T\xfcrkiye", 
"T\xfcrkiye", "T\xfcrkiye", "T\xfcrkiye", "T\xfcrkiye", "T\xfcrkiye", 
"T\xfcrkiye", "T\xfcrkiye", "T\xfcrkiye", "T\xfcrkiye", "T\xfcrkiye", 
"T\xfcrkiye", "T\xfcrkiye", "T\xfcrkiye", "T\xfcrkiye", "T\xfcrkiye", 
"T\xfcrkiye", "T\xfcrkiye", "T\xfcrkiye", "T\xfcrkiye", "Turkmenistan", 
"Turkmenistan", "Turkmenistan", "Turkmenistan", "Turkmenistan", 
"Turkmenistan", "Turkmenistan", "Turkmenistan", "Turkmenistan", 
"Turkmenistan", "Turkmenistan", "Turkmenistan", "Turkmenistan", 
"Turkmenistan", "Turkmenistan", "Turkmenistan", "Turkmenistan", 
"Turkmenistan", "Turkmenistan", "Turkmenistan", "Turkmenistan", 
"Turkmenistan", "Turkmenistan", "Turkmenistan", "Turkmenistan", 
"Turkmenistan", "Turkmenistan", "Turkmenistan", "Turkmenistan", 
"Turkmenistan", "Turkmenistan", "Turkmenistan", "Turks and Caicos Islands", 
"Turks and Caicos Islands", "Turks and Caicos Islands", "Turks and Caicos Islands", 
"Turks and Caicos Islands", "Turks and Caicos Islands", "Turks and Caicos Islands", 
"Turks and Caicos Islands", "Turks and Caicos Islands", "Turks and Caicos Islands", 
"Turks and Caicos Islands", "Turks and Caicos Islands", "Turks and Caicos Islands", 
"Turks and Caicos Islands", "Turks and Caicos Islands", "Turks and Caicos Islands", 
"Turks and Caicos Islands", "Turks and Caicos Islands", "Turks and Caicos Islands", 
"Tuvalu", "Tuvalu", "Tuvalu", "Tuvalu", "Tuvalu", "Tuvalu", "Tuvalu", 
"Tuvalu", "Uganda", "Uganda", "Uganda", "Uganda", "Uganda", "Uganda", 
"Uganda", "Uganda", "Uganda", "Uganda", "Uganda", "Uganda", "Uganda", 
"Uganda", "Uganda", "Uganda", "Uganda", "Uganda", "Uganda", "Uganda", 
"Uganda", "Uganda", "Uganda", "Uganda", "Uganda", "Uganda", "Uganda", 
"Uganda", "Uganda", "Uganda", "Uganda", "Uganda", "Uganda", "Uganda", 
"Uganda", "Uganda", "Ukraine", "Ukraine", "Ukraine", "Ukraine", 
"Ukraine", "Ukraine", "Ukraine", "Ukraine", "Ukraine", "Ukraine", 
"Ukraine", "Ukraine", "Ukraine", "Ukraine", "Ukraine", "Ukraine", 
"Ukraine", "Ukraine", "Ukraine", "Ukraine", "Ukraine", "Ukraine", 
"Ukraine", "Ukraine", "Ukraine", "Ukraine", "Ukraine", "Ukraine", 
"Ukraine", "Ukraine", "Ukraine", "Ukraine", "Ukraine", "Ukraine", 
"Ukraine", "Ukraine", "United Arab Emirates", "United Arab Emirates", 
"United Arab Emirates", "United Arab Emirates", "United Arab Emirates", 
"United Arab Emirates", "United Arab Emirates", "United Arab Emirates", 
"United Arab Emirates", "United Arab Emirates", "United Arab Emirates", 
"United Arab Emirates", "United Arab Emirates", "United Arab Emirates", 
"United Arab Emirates", "United Arab Emirates", "United Arab Emirates", 
"United Arab Emirates", "United Arab Emirates", "United Arab Emirates", 
"United Arab Emirates", "United Arab Emirates", "United Arab Emirates", 
"United Arab Emirates", "United Arab Emirates", "United Arab Emirates", 
"United Arab Emirates", "United Arab Emirates", "United Arab Emirates", 
"United Arab Emirates", "United Arab Emirates", "United Arab Emirates", 
"United Arab Emirates", "United Kingdom", "United Kingdom", "United Kingdom", 
"United Kingdom", "United Kingdom", "United Kingdom", "United Kingdom", 
"United Kingdom", "United Kingdom", "United Kingdom", "United Kingdom", 
"United Kingdom", "United Kingdom", "United Kingdom", "United Kingdom", 
"United Kingdom", "United Kingdom", "United Kingdom", "United Kingdom", 
"United Kingdom", "United Kingdom", "United Kingdom", "United Kingdom", 
"United Kingdom", "United Kingdom", "United Kingdom", "United Kingdom", 
"United Kingdom", "United Kingdom", "United Kingdom", "United Kingdom", 
"United Kingdom", "United Kingdom", "United Kingdom", "United Kingdom", 
"United Kingdom", "United Rep. of Tanzania", "United Rep. of Tanzania", 
"United Rep. of Tanzania", "United Rep. of Tanzania", "United Rep. of Tanzania", 
"United Rep. of Tanzania", "United Rep. of Tanzania", "United Rep. of Tanzania", 
"United Rep. of Tanzania", "United Rep. of Tanzania", "United Rep. of Tanzania", 
"United Rep. of Tanzania", "United Rep. of Tanzania", "United Rep. of Tanzania", 
"United Rep. of Tanzania", "United Rep. of Tanzania", "United Rep. of Tanzania", 
"United Rep. of Tanzania", "United Rep. of Tanzania", "United Rep. of Tanzania", 
"United Rep. of Tanzania", "United Rep. of Tanzania", "United Rep. of Tanzania", 
"United Rep. of Tanzania", "United Rep. of Tanzania", "United Rep. of Tanzania", 
"United Rep. of Tanzania", "United Rep. of Tanzania", "United Rep. of Tanzania", 
"United Rep. of Tanzania", "United Rep. of Tanzania", "United Rep. of Tanzania", 
"United Rep. of Tanzania", "United Rep. of Tanzania", "United Rep. of Tanzania", 
"United Rep. of Tanzania", "United States of America", "United States of America", 
"United States of America", "United States of America", "United States of America", 
"United States of America", "United States of America", "United States of America", 
"United States of America", "United States of America", "United States of America", 
"United States of America", "United States of America", "United States of America", 
"United States of America", "United States of America", "United States of America", 
"United States of America", "United States of America", "United States of America", 
"United States of America", "United States of America", "United States of America", 
"United States of America", "United States of America", "United States of America", 
"United States of America", "United States of America", "United States of America", 
"United States of America", "United States of America", "United States of America", 
"United States Virgin Islands", "United States Virgin Islands", 
"United States Virgin Islands", "United States Virgin Islands", 
"United States Virgin Islands", "United States Virgin Islands", 
"United States Virgin Islands", "United States Virgin Islands", 
"United States Virgin Islands", "United States Virgin Islands", 
"United States Virgin Islands", "United States Virgin Islands", 
"United States Virgin Islands", "United States Virgin Islands", 
"United States Virgin Islands", "United States Virgin Islands", 
"Uruguay", "Uruguay", "Uruguay", "Uruguay", "Uruguay", "Uruguay", 
"Uruguay", "Uruguay", "Uruguay", "Uruguay", "Uruguay", "Uruguay", 
"Uruguay", "Uruguay", "Uruguay", "Uruguay", "Uruguay", "Uruguay", 
"Uruguay", "Uruguay", "Uruguay", "Uruguay", "Uruguay", "Uruguay", 
"Uruguay", "Uruguay", "Uruguay", "Uruguay", "Uruguay", "Uruguay", 
"Uruguay", "Uruguay", "Uruguay", "Uzbekistan", "Uzbekistan", 
"Uzbekistan", "Uzbekistan", "Uzbekistan", "Uzbekistan", "Uzbekistan", 
"Uzbekistan", "Uzbekistan", "Uzbekistan", "Uzbekistan", "Uzbekistan", 
"Uzbekistan", "Uzbekistan", "Uzbekistan", "Uzbekistan", "Uzbekistan", 
"Uzbekistan", "Uzbekistan", "Uzbekistan", "Uzbekistan", "Uzbekistan", 
"Uzbekistan", "Uzbekistan", "Uzbekistan", "Uzbekistan", "Uzbekistan", 
"Uzbekistan", "Uzbekistan", "Uzbekistan", "Uzbekistan", "Uzbekistan", 
"Vanuatu", "Vanuatu", "Vanuatu", "Vanuatu", "Vanuatu", "Vanuatu", 
"Vanuatu", "Vanuatu", "Vanuatu", "Vanuatu", "Vanuatu", "Vanuatu", 
"Vanuatu", "Vanuatu", "Vanuatu", "Vanuatu", "Vanuatu", "Vanuatu", 
"Vanuatu", "Vanuatu", "Vanuatu", "Vanuatu", "Venezuela (Boliv. Rep. of)", 
"Venezuela (Boliv. Rep. of)", "Venezuela (Boliv. Rep. of)", "Venezuela (Boliv. Rep. of)", 
"Venezuela (Boliv. Rep. of)", "Venezuela (Boliv. Rep. of)", "Venezuela (Boliv. Rep. of)", 
"Venezuela (Boliv. Rep. of)", "Venezuela (Boliv. Rep. of)", "Venezuela (Boliv. Rep. of)", 
"Venezuela (Boliv. Rep. of)", "Venezuela (Boliv. Rep. of)", "Venezuela (Boliv. Rep. of)", 
"Venezuela (Boliv. Rep. of)", "Venezuela (Boliv. Rep. of)", "Venezuela (Boliv. Rep. of)", 
"Venezuela (Boliv. Rep. of)", "Venezuela (Boliv. Rep. of)", "Venezuela (Boliv. Rep. of)", 
"Venezuela (Boliv. Rep. of)", "Venezuela (Boliv. Rep. of)", "Venezuela (Boliv. Rep. of)", 
"Venezuela (Boliv. Rep. of)", "Venezuela (Boliv. Rep. of)", "Venezuela (Boliv. Rep. of)", 
"Venezuela (Boliv. Rep. of)", "Venezuela (Boliv. Rep. of)", "Venezuela (Boliv. Rep. of)", 
"Venezuela (Boliv. Rep. of)", "Venezuela (Boliv. Rep. of)", "Venezuela (Boliv. Rep. of)", 
"Venezuela (Boliv. Rep. of)", "Venezuela (Boliv. Rep. of)", "Venezuela (Boliv. Rep. of)", 
"Viet Nam", "Viet Nam", "Viet Nam", "Viet Nam", "Viet Nam", "Viet Nam", 
"Viet Nam", "Viet Nam", "Viet Nam", "Viet Nam", "Viet Nam", "Viet Nam", 
"Viet Nam", "Viet Nam", "Viet Nam", "Viet Nam", "Viet Nam", "Viet Nam", 
"Viet Nam", "Viet Nam", "Viet Nam", "Viet Nam", "Viet Nam", "Viet Nam", 
"Viet Nam", "Viet Nam", "Viet Nam", "Viet Nam", "Viet Nam", "Wallis and Futuna Islands", 
"Wallis and Futuna Islands", "Wallis and Futuna Islands", "Wallis and Futuna Islands", 
"Wallis and Futuna Islands", "Wallis and Futuna Islands", "Wallis and Futuna Islands", 
"Wallis and Futuna Islands", "Western Sahara", "Western Sahara", 
"Western Sahara", "Western Sahara", "Western Sahara", "Western Sahara", 
"Western Sahara", "Western Sahara", "Western Sahara", "Western Sahara", 
"Western Sahara", "Western Sahara", "Western Sahara", "Western Sahara", 
"Western Sahara", "Western Sahara", "Yemen", "Yemen", "Yemen", 
"Yemen", "Yemen", "Yemen", "Yemen", "Yemen", "Yemen", "Yemen", 
"Yemen", "Yemen", "Yemen", "Yemen", "Yemen", "Yemen", "Yemen", 
"Yemen", "Yemen", "Yemen", "Yemen", "Yemen", "Yemen", "Yemen", 
"Yemen", "Yemen", "Yemen", "Yemen", "Yemen", "Yemen", "Yemen", 
"Yemen", "Yemen", "Yemen", "Yemen", "Yemen", "Zambia", "Zambia", 
"Zambia", "Zambia", "Zambia", "Zambia", "Zambia", "Zambia", "Zambia", 
"Zambia", "Zambia", "Zambia", "Zambia", "Zambia", "Zambia", "Zambia", 
"Zambia", "Zambia", "Zambia", "Zambia", "Zambia", "Zambia", "Zambia", 
"Zambia", "Zambia", "Zambia", "Zambia", "Zambia", "Zambia", "Zambia", 
"Zambia", "Zambia", "Zambia", "Zambia", "Zambia", "Zambia", "Zimbabwe", 
"Zimbabwe", "Zimbabwe", "Zimbabwe", "Zimbabwe", "Zimbabwe", "Zimbabwe", 
"Zimbabwe", "Zimbabwe", "Zimbabwe", "Zimbabwe", "Zimbabwe", "Zimbabwe", 
"Zimbabwe", "Zimbabwe", "Zimbabwe", "Zimbabwe", "Zimbabwe", "Zimbabwe", 
"Zimbabwe", "Zimbabwe", "Zimbabwe", "Zimbabwe", "Zimbabwe", "Zimbabwe", 
"Zimbabwe", "Zimbabwe", "Zimbabwe", "Zimbabwe", "Zimbabwe", "Zimbabwe", 
"Zimbabwe", "Zimbabwe", "Zimbabwe", "Zimbabwe"), ISO2C = c("AF", 
"AF", "AF", "AF", "AF", "AF", "AF", "AF", "AF", "AF", "AF", "AF", 
"AF", "AF", "AF", "AF", "AF", "AF", "AF", "AF", "AF", "AF", "AF", 
"AF", "AF", "AF", "AF", "AF", "AF", "AF", "AF", "AF", "AF", "AF", 
"AF", "AF", "AL", "AL", "AL", "AL", "AL", "AL", "AL", "AL", "AL", 
"AL", "AL", "AL", "AL", "AL", "AL", "AL", "AL", "AL", "AL", "AL", 
"AL", "AL", "AL", "AL", "AL", "AL", "AL", "AL", "AL", "AL", "AL", 
"AL", "AL", "AL", "AL", "DZ", "DZ", "DZ", "DZ", "DZ", "DZ", "DZ", 
"DZ", "DZ", "DZ", "DZ", "DZ", "DZ", "DZ", "DZ", "DZ", "DZ", "DZ", 
"DZ", "DZ", "DZ", "DZ", "DZ", "DZ", "DZ", "DZ", "DZ", "DZ", "DZ", 
"DZ", "DZ", "AS", "AS", "AS", "AS", "AS", "AS", "AS", "AS", "AD", 
"AD", "AD", "AD", "AD", "AD", "AD", "AD", "AO", "AO", "AO", "AO", 
"AO", "AO", "AO", "AO", "AO", "AO", "AO", "AO", "AO", "AO", "AO", 
"AO", "AO", "AO", "AO", "AO", "AO", "AO", "AO", "AO", "AO", "AO", 
"AO", "AO", "AO", "AO", "AO", "AO", "AO", "AO", "AO", "AI", "AI", 
"AI", "AI", "AI", "AI", "AI", "AI", "AI", "AI", "AI", "AI", "AI", 
"AI", "AG", "AG", "AG", "AG", "AG", "AG", "AG", "AG", "AG", "AG", 
"AG", "AG", "AG", "AG", "AG", "AG", "AG", "AG", "AG", "AG", "AG", 
"AG", "AG", "AR", "AR", "AR", "AR", "AR", "AR", "AR", "AR", "AR", 
"AR", "AR", "AR", "AR", "AR", "AR", "AR", "AR", "AR", "AR", "AR", 
"AR", "AR", "AR", "AR", "AR", "AR", "AR", "AR", "AR", "AR", "AR", 
"AR", "AR", "AR", "AM", "AM", "AM", "AM", "AM", "AM", "AM", "AM", 
"AM", "AM", "AM", "AM", "AM", "AM", "AM", "AM", "AM", "AM", "AM", 
"AM", "AM", "AM", "AM", "AM", "AM", "AM", "AM", "AM", "AM", "AM", 
"AM", "AM", "AM", "AM", "AM", "AW", "AW", "AW", "AW", "AW", "AW", 
"AW", "AW", "AW", "AW", "AW", "AW", "AW", "AW", "AW", "AW", "AW", 
"AW", "AW", "AW", "AW", "AW", "AW", "AW", "AW", "AW", "AW", "AW", 
"AW", "AW", "AU", "AU", "AU", "AU", "AU", "AU", "AU", "AU", "AU", 
"AU", "AU", "AU", "AU", "AU", "AU", "AU", "AU", "AU", "AU", "AU", 
"AU", "AU", "AU", "AU", "AU", "AU", "AU", "AU", "AU", "AU", "AU", 
"AU", "AU", "AU", "AT", "AT", "AT", "AT", "AT", "AT", "AT", "AT", 
"AT", "AT", "AT", "AT", "AT", "AT", "AT", "AT", "AT", "AT", "AT", 
"AT", "AT", "AT", "AT", "AT", "AT", "AT", "AT", "AT", "AT", "AT", 
"AT", "AT", "AT", "AT", "AT", "AT", "AZ", "AZ", "AZ", "AZ", "AZ", 
"AZ", "AZ", "AZ", "AZ", "AZ", "AZ", "AZ", "AZ", "AZ", "AZ", "AZ", 
"AZ", "AZ", "AZ", "AZ", "AZ", "AZ", "AZ", "AZ", "AZ", "AZ", "AZ", 
"AZ", "AZ", "AZ", "AZ", "AZ", "AZ", "AZ", "AZ", "AZ", "BS", "BS", 
"BS", "BS", "BS", "BS", "BS", "BS", "BS", "BS", "BS", "BS", "BS", 
"BS", "BS", "BS", "BS", "BS", "BS", "BS", "BS", "BS", "BS", "BS", 
"BS", "BS", "BS", "BS", "BS", "BS", "BS", "BS", "BS", "BS", "BS", 
"BH", "BH", "BH", "BH", "BH", "BH", "BH", "BH", "BH", "BH", "BH", 
"BH", "BH", "BH", "BH", "BH", "BH", "BH", "BH", "BH", "BH", "BH", 
"BH", "BH", "BH", "BH", "BH", "BH", "BH", "BH", "BD", "BD", "BD", 
"BD", "BD", "BD", "BD", "BD", "BD", "BD", "BD", "BD", "BD", "BD", 
"BD", "BD", "BD", "BD", "BD", "BD", "BD", "BD", "BD", "BD", "BD", 
"BD", "BD", "BD", "BD", "BD", "BD", "BD", "BB", "BB", "BB", "BB", 
"BB", "BB", "BB", "BB", "BB", "BB", "BB", "BB", "BB", "BB", "BB", 
"BB", "BB", "BB", "BB", "BB", "BB", "BB", "BB", "BB", "BB", "BY", 
"BY", "BY", "BY", "BY", "BY", "BY", "BY", "BY", "BY", "BY", "BY", 
"BY", "BY", "BY", "BY", "BY", "BY", "BY", "BY", "BY", "BY", "BY", 
"BY", "BY", "BY", "BY", "BY", "BY", "BY", "BY", "BY", "BY", "BY", 
"BY", "BY", "BE", "BE", "BE", "BE", "BE", "BE", "BE", "BE", "BE", 
"BE", "BE", "BE", "BE", "BE", "BE", "BE", "BE", "BE", "BE", "BE", 
"BE", "BE", "BE", "BE", "BE", "BE", "BE", "BE", "BE", "BE", "BE", 
"BE", "BE", "BE", "BE", "BE", "BZ", "BZ", "BZ", "BZ", "BZ", "BZ", 
"BZ", "BZ", "BZ", "BZ", "BZ", "BZ", "BZ", "BZ", "BZ", "BZ", "BZ", 
"BZ", "BZ", "BZ", "BZ", "BZ", "BZ", "BZ", "BZ", "BZ", "BZ", "BZ", 
"BZ", "BZ", "BZ", "BZ", "BZ", "BJ", "BJ", "BJ", "BJ", "BJ", "BJ", 
"BJ", "BJ", "BJ", "BJ", "BJ", "BJ", "BJ", "BJ", "BJ", "BJ", "BJ", 
"BJ", "BJ", "BJ", "BJ", "BJ", "BJ", "BJ", "BJ", "BJ", "BJ", "BJ", 
"BJ", "BJ", "BJ", "BJ", "BJ", "BM", "BM", "BM", "BM", "BM", "BM", 
"BM", "BM", "BT", "BT", "BT", "BT", "BT", "BT", "BT", "BT", "BT", 
"BT", "BT", "BT", "BT", "BT", "BT", "BT", "BO", "BO", "BO", "BO", 
"BO", "BO", "BO", "BO", "BO", "BO", "BO", "BO", "BO", "BO", "BO", 
"BO", "BO", "BO", "BO", "BO", "BO", "BO", "BO", "BO", "BO", "BO", 
"BO", "BO", "BO", "BO", "BO", "BO", "BO", "BO", "BO", "BQ", "BQ", 
"BQ", "BQ", "BQ", "BQ", "BQ", "BQ", "BQ", "BQ", "BA", "BA", "BA", 
"BA", "BA", "BA", "BA", "BA", "BA", "BA", "BA", "BA", "BA", "BA", 
"BA", "BA", "BA", "BA", "BA", "BA", "BA", "BA", "BA", "BA", "BA", 
"BA", "BA", "BA", "BA", "BA", "BA", "BA", "BA", "BA", "BA", "BA", 
"BW", "BW", "BW", "BW", "BW", "BW", "BW", "BW", "BW", "BW", "BW", 
"BW", "BW", "BW", "BW", "BW", "BW", "BW", "BW", "BW", "BW", "BW", 
"BW", "BW", "BW", "BW", "BW", "BW", "BW", "BW", "BW", "BW", "BW", 
"BW", "BW", "BR", "BR", "BR", "BR", "BR", "BR", "BR", "BR", "BR", 
"BR", "BR", "BR", "BR", "BR", "BR", "BR", "BR", "BR", "BR", "BR", 
"BR", "BR", "BR", "BR", "BR", "BR", "BR", "BR", "BR", "BR", "BR", 
"BR", "BR", "BR", "BR", "BR", "VG", "VG", "VG", "VG", "VG", "VG", 
"VG", "VG", "VG", "VG", "VG", "VG", "VG", "VG", "VG", "VG", "VG", 
"VG", "BN", "BN", "BN", "BN", "BN", "BN", "BN", "BN", "BN", "BN", 
"BN", "BN", "BN", "BN", "BN", "BN", "BN", "BN", "BN", "BN", "BN", 
"BN", "BN", "BN", "BG", "BG", "BG", "BG", "BG", "BG", "BG", "BG", 
"BG", "BG", "BG", "BG", "BG", "BG", "BG", "BG", "BG", "BG", "BG", 
"BG", "BG", "BG", "BG", "BG", "BG", "BG", "BG", "BG", "BG", "BG", 
"BG", "BG", "BG", "BG", "BF", "BF", "BF", "BF", "BF", "BF", "BF", 
"BF", "BF", "BF", "BF", "BF", "BF", "BF", "BF", "BF", "BF", "BF", 
"BF", "BF", "BF", "BF", "BF", "BF", "BF", "BF", "BF", "BF", "BF", 
"BF", "BF", "BF", "BF", "BF", "BF", "BI", "BI", "BI", "BI", "BI", 
"BI", "BI", "BI", "BI", "BI", "BI", "BI", "BI", "BI", "BI", "BI", 
"BI", "BI", "BI", "BI", "BI", "BI", "BI", "BI", "BI", "BI", "BI", 
"BI", "BI", "BI", "BI", "BI", "BI", "BI", "BI", "BI", "CV", "CV", 
"CV", "CV", "CV", "CV", "CV", "CV", "CV", "CV", "CV", "CV", "CV", 
"CV", "CV", "CV", "CV", "CV", "CV", "CV", "CV", "CV", "CV", "CV", 
"KH", "KH", "KH", "KH", "KH", "KH", "KH", "KH", "KH", "KH", "KH", 
"KH", "KH", "KH", "KH", "KH", "KH", "KH", "KH", "KH", "KH", "KH", 
"KH", "KH", "KH", "KH", "KH", "KH", "KH", "KH", "KH", "KH", "KH", 
"KH", "CM", "CM", "CM", "CM", "CM", "CM", "CM", "CM", "CM", "CM", 
"CM", "CM", "CM", "CM", "CM", "CM", "CM", "CM", "CM", "CM", "CM", 
"CM", "CM", "CM", "CM", "CM", "CM", "CM", "CM", "CM", "CM", "CM", 
"CM", "CM", "CM", "CM", "CA", "CA", "CA", "CA", "CA", "CA", "CA", 
"CA", "CA", "CA", "CA", "CA", "CA", "CA", "CA", "CA", "CA", "CA", 
"CA", "CA", "CA", "CA", "CA", "CA", "CA", "CA", "CA", "CA", "CA", 
"CA", "CA", "CA", "CA", "CA", "CA", "KY", "KY", "KY", "KY", "KY", 
"KY", "KY", "KY", "KY", "KY", "KY", "KY", "KY", "KY", "KY", "KY", 
"KY", "KY", "KY", "KY", "KY", "KY", "KY", "CF", "CF", "CF", "CF", 
"CF", "CF", "CF", "CF", "CF", "CF", "CF", "CF", "CF", "CF", "CF", 
"CF", "CF", "CF", "CF", "CF", "CF", "CF", "CF", "CF", "CF", "CF", 
"CF", "CF", "CF", "CF", "CF", "CF", "CF", "CF", "CF", "CF", "TD", 
"TD", "TD", "TD", "TD", "TD", "TD", "TD", "TD", "TD", "TD", "TD", 
"TD", "TD", "TD", "TD", "TD", "TD", "TD", "TD", "TD", "TD", "TD", 
"TD", "TD", "TD", "TD", "TD", "TD", "TD", "TD", "TD", "TD", "TD", 
"TD", "CL", "CL", "CL", "CL", "CL", "CL", "CL", "CL", "CL", "CL", 
"CL", "CL", "CL", "CL", "CL", "CL", "CL", "CL", "CL", "CL", "CL", 
"CL", "CL", "CL", "CL", "CL", "CL", "CL", "CL", "CL", "CL", "CL", 
"CL", "CN", "CN", "CN", "CN", "CN", "CN", "CN", "CN", "CN", "CN", 
"CN", "CN", "CN", "CN", "CN", "CN", "CN", "CN", "CN", "CN", "CN", 
"CN", "CN", "CN", "CN", "CN", "CN", "CN", "CN", "CN", "CN", "CN", 
"HK", "HK", "HK", "HK", "HK", "HK", "HK", "HK", "HK", "HK", "HK", 
"HK", "HK", "HK", "HK", "HK", "HK", "HK", "HK", "HK", "HK", "HK", 
"HK", "HK", "HK", "HK", "HK", "HK", "HK", "HK", "HK", "HK", "HK", 
"HK", "HK", "HK", "HK", "HK", "MO", "MO", "MO", "MO", "MO", "MO", 
"MO", "MO", "MO", "MO", "MO", "MO", "MO", "MO", "MO", "MO", "MO", 
"MO", "MO", "MO", "MO", "MO", "MO", "CO", "CO", "CO", "CO", "CO", 
"CO", "CO", "CO", "CO", "CO", "CO", "CO", "CO", "CO", "CO", "CO", 
"CO", "CO", "CO", "CO", "CO", "CO", "CO", "CO", "CO", "CO", "CO", 
"CO", "CO", "CO", "CO", "CO", "CO", "CO", "CO", "CO", "KM", "KM", 
"KM", "KM", "KM", "KM", "KM", "KM", "KM", "KM", "KM", "KM", "KM", 
"KM", "KM", "KM", "KM", "KM", "KM", "KM", "CG", "CG", "CG", "CG", 
"CG", "CG", "CG", "CG", "CG", "CG", "CG", "CG", "CG", "CG", "CG", 
"CG", "CG", "CG", "CG", "CG", "CG", "CG", "CG", "CG", "CG", "CG", 
"CG", "CG", "CG", "CG", "CG", "CG", "CG", "CG", "CG", "CG", "CK", 
"CK", "CK", "CK", "CK", "CK", "CK", "CK", "CR", "CR", "CR", "CR", 
"CR", "CR", "CR", "CR", "CR", "CR", "CR", "CR", "CR", "CR", "CR", 
"CR", "CR", "CR", "CR", "CR", "CR", "CR", "CR", "CR", "CR", "CR", 
"CR", "CR", "CR", "CR", "CR", "CR", "CR", "CR", "CR", "CI", "CI", 
"CI", "CI", "CI", "CI", "CI", "CI", "CI", "CI", "CI", "CI", "CI", 
"CI", "CI", "CI", "CI", "CI", "CI", "CI", "CI", "CI", "CI", "CI", 
"CI", "CI", "CI", "CI", "CI", "CI", "CI", "CI", "CI", "CI", "CI", 
"CI", "HR", "HR", "HR", "HR", "HR", "HR", "HR", "HR", "HR", "HR", 
"HR", "HR", "HR", "HR", "HR", "HR", "HR", "HR", "HR", "HR", "HR", 
"HR", "HR", "HR", "HR", "HR", "HR", "HR", "HR", "HR", "HR", "HR", 
"HR", "HR", "HR", "HR", "CU", "CU", "CU", "CU", "CU", "CU", "CU", 
"CU", "CU", "CU", "CU", "CU", "CU", "CU", "CU", "CU", "CU", "CU", 
"CU", "CU", "CU", "CU", "CU", "CU", "CU", "CU", "CU", "CU", "CU", 
"CU", "CU", "CU", "CU", "CW", "CW", "CW", "CW", "CW", "CW", "CW", 
"CW", "CW", "CW", "CW", "CW", "CW", "CW", "CW", "CW", "CW", "CW", 
"CW", "CW", "CW", "CW", "CW", "CW", "CW", "CW", "CW", "CW", "CY", 
"CY", "CY", "CY", "CY", "CY", "CY", "CY", "CY", "CY", "CY", "CY", 
"CY", "CY", "CY", "CY", "CY", "CY", "CY", "CY", "CY", "CY", "CY", 
"CY", "CY", "CY", "CY", "CY", "CY", "CY", "CY", "CY", "CY", "CY", 
"CY", "CZ", "CZ", "CZ", "CZ", "CZ", "CZ", "CZ", "CZ", "CZ", "CZ", 
"CZ", "CZ", "CZ", "CZ", "CZ", "CZ", "CZ", "CZ", "CZ", "CZ", "CZ", 
"CZ", "CZ", "CZ", "CZ", "CZ", "CZ", "CZ", "CZ", "CZ", "CZ", "CZ", 
"CZ", "CZ", "CZ", "KP", "KP", "KP", "KP", "KP", "KP", "KP", "KP", 
"KP", "KP", "KP", "KP", "KP", "KP", "KP", "KP", "CD", "CD", "CD", 
"CD", "CD", "CD", "CD", "CD", "CD", "CD", "CD", "CD", "CD", "CD", 
"CD", "CD", "CD", "CD", "CD", "CD", "CD", "CD", "CD", "CD", "CD", 
"CD", "CD", "CD", "CD", "CD", "CD", "CD", "CD", "CD", "CD", "CD", 
"DK", "DK", "DK", "DK", "DK", "DK", "DK", "DK", "DK", "DK", "DK", 
"DK", "DK", "DK", "DK", "DK", "DK", "DK", "DK", "DK", "DK", "DK", 
"DK", "DK", "DK", "DK", "DK", "DK", "DK", "DK", "DK", "DK", "DK", 
"DK", "DK", "DK", "DJ", "DJ", "DJ", "DJ", "DJ", "DJ", "DJ", "DJ", 
"DJ", "DJ", "DJ", "DJ", "DJ", "DJ", "DJ", "DJ", "DJ", "DJ", "DJ", 
"DJ", "DJ", "DJ", "DJ", "DJ", "DJ", "DJ", "DJ", "DJ", "DJ", "DJ", 
"DJ", "DJ", "DJ", "DJ", "DJ", "DJ", "DJ", "DM", "DM", "DM", "DM", 
"DM", "DM", "DM", "DM", "DM", "DM", "DM", "DO", "DO", "DO", "DO", 
"DO", "DO", "DO", "DO", "DO", "DO", "DO", "DO", "DO", "DO", "DO", 
"DO", "DO", "DO", "DO", "DO", "DO", "DO", "DO", "DO", "DO", "DO", 
"DO", "DO", "DO", "DO", "DO", "EC", "EC", "EC", "EC", "EC", "EC", 
"EC", "EC", "EC", "EC", "EC", "EC", "EC", "EC", "EC", "EC", "EC", 
"EC", "EC", "EC", "EC", "EC", "EC", "EC", "EC", "EC", "EC", "EC", 
"EC", "EC", "EC", "EC", "EC", "EC", "EG", "EG", "EG", "EG", "EG", 
"EG", "EG", "EG", "EG", "EG", "EG", "EG", "EG", "EG", "EG", "EG", 
"EG", "EG", "EG", "EG", "EG", "EG", "EG", "EG", "EG", "EG", "EG", 
"EG", "EG", "EG", "EG", "EG", "EG", "EG", "EG", "SV", "SV", "SV", 
"SV", "SV", "SV", "SV", "SV", "SV", "SV", "SV", "SV", "SV", "SV", 
"SV", "SV", "SV", "SV", "SV", "SV", "SV", "SV", "SV", "SV", "SV", 
"SV", "SV", "SV", "SV", "SV", "SV", "SV", "SV", "GQ", "GQ", "GQ", 
"GQ", "GQ", "GQ", "GQ", "GQ", "GQ", "GQ", "GQ", "GQ", "GQ", "GQ", 
"GQ", "GQ", "ER", "ER", "ER", "ER", "ER", "ER", "ER", "ER", "ER", 
"ER", "ER", "ER", "ER", "ER", "ER", "ER", "ER", "ER", "ER", "ER", 
"ER", "ER", "ER", "ER", "ER", "ER", "ER", "ER", "ER", "ER", "ER", 
"ER", "ER", "ER", "ER", "ER", "ER", "ER", "EE", "EE", "EE", "EE", 
"EE", "EE", "EE", "EE", "EE", "EE", "EE", "EE", "EE", "EE", "EE", 
"EE", "EE", "EE", "EE", "EE", "EE", "EE", "EE", "EE", "EE", "EE", 
"EE", "EE", "EE", "EE", "EE", "EE", "EE", "EE", "EE", "EE", "SZ", 
"SZ", "SZ", "SZ", "SZ", "SZ", "SZ", "SZ", "SZ", "SZ", "SZ", "SZ", 
"SZ", "SZ", "SZ", "SZ", "SZ", "SZ", "SZ", "SZ", "SZ", "SZ", "SZ", 
"SZ", "SZ", "SZ", "SZ", "SZ", "SZ", "SZ", "SZ", "SZ", "ET", "ET", 
"ET", "ET", "ET", "ET", "ET", "ET", "ET", "ET", "ET", "ET", "ET", 
"ET", "ET", "ET", "ET", "ET", "ET", "ET", "ET", "ET", "ET", "ET", 
"ET", "ET", "ET", "ET", "ET", "ET", "ET", "ET", "ET", "ET", "ET", 
"ET", "FK", "FK", "FK", "FK", "FK", "FK", "FK", "FK", "FO", "FO", 
"FO", "FO", "FO", "FO", "FO", "FO", "FJ", "FJ", "FJ", "FJ", "FJ", 
"FJ", "FJ", "FJ", "FJ", "FJ", "FJ", "FJ", "FJ", "FJ", "FJ", "FJ", 
"FJ", "FJ", "FJ", "FJ", "FJ", "FJ", "FJ", "FJ", "FJ", "FJ", "FJ", 
"FJ", "FJ", "FJ", "FI", "FI", "FI", "FI", "FI", "FI", "FI", "FI", 
"FI", "FI", "FI", "FI", "FI", "FI", "FI", "FI", "FI", "FI", "FI", 
"FI", "FI", "FI", "FI", "FI", "FI", "FI", "FI", "FI", "FI", "FI", 
"FI", "FI", "FI", "FI", "FI", "FR", "FR", "FR", "FR", "FR", "FR", 
"FR", "FR", "FR", "FR", "FR", "FR", "FR", "FR", "FR", "FR", "FR", 
"FR", "FR", "FR", "FR", "FR", "FR", "FR", "FR", "FR", "FR", "FR", 
"FR", "FR", "FR", "FR", "FR", "FR", "FR", "FR", "GF", "GF", "GF", 
"GF", "GF", "GF", "GF", "GF", "GF", "GF", "GF", "GF", "GF", "GF", 
"GF", "GF", "PF", "PF", "PF", "PF", "PF", "PF", "PF", "PF", "PF", 
"PF", "PF", "PF", "PF", "PF", "PF", "PF", "GA", "GA", "GA", "GA", 
"GA", "GA", "GA", "GA", "GA", "GA", "GA", "GA", "GA", "GA", "GA", 
"GA", "GA", "GA", "GA", "GA", "GA", "GA", "GA", "GA", "GA", "GA", 
"GA", "GA", "GA", "GA", "GA", "GA", "GA", "GA", "GA", "GA", "GA", 
"GM", "GM", "GM", "GM", "GM", "GM", "GM", "GM", "GM", "GM", "GM", 
"GM", "GM", "GM", "GM", "GM", "GM", "GM", "GM", "GM", "GM", "GM", 
"GM", "GM", "GM", "GM", "GM", "GM", "GM", "GM", "GM", "GM", "GM", 
"GM", "GM", "GM", "GM", "GE", "GE", "GE", "GE", "GE", "GE", "GE", 
"GE", "GE", "GE", "GE", "GE", "GE", "GE", "GE", "GE", "GE", "GE", 
"GE", "GE", "GE", "GE", "GE", "GE", "GE", "GE", "GE", "GE", "GE", 
"GE", "GE", "GE", "GE", "GE", "GE", "GE", "DE", "DE", "DE", "DE", 
"DE", "DE", "DE", "DE", "DE", "DE", "DE", "DE", "DE", "DE", "DE", 
"DE", "DE", "DE", "DE", "DE", "DE", "DE", "DE", "DE", "DE", "DE", 
"DE", "DE", "DE", "DE", "DE", "DE", "DE", "DE", "DE", "DE", "GH", 
"GH", "GH", "GH", "GH", "GH", "GH", "GH", "GH", "GH", "GH", "GH", 
"GH", "GH", "GH", "GH", "GH", "GH", "GH", "GH", "GH", "GH", "GH", 
"GH", "GH", "GH", "GH", "GH", "GH", "GH", "GH", "GH", "GH", "GH", 
"GH", "GH", "GH", "GI", "GI", "GI", "GI", "GI", "GI", "GI", "GI", 
"GR", "GR", "GR", "GR", "GR", "GR", "GR", "GR", "GR", "GR", "GR", 
"GR", "GR", "GR", "GR", "GR", "GR", "GR", "GR", "GR", "GR", "GR", 
"GR", "GR", "GR", "GR", "GR", "GR", "GR", "GR", "GR", "GR", "GR", 
"GR", "GR", "GR", "GL", "GL", "GL", "GL", "GL", "GL", "GL", "GL", 
"GD", "GD", "GD", "GD", "GD", "GD", "GD", "GD", "GD", "GD", "GD", 
"GD", "GD", "GD", "GD", "GD", "GD", "GD", "GD", "GD", "GD", "GD", 
"GD", "GD", "GD", "GP", "GP", "GP", "GP", "GP", "GP", "GP", "GP", 
"GP", "GP", "GP", "GP", "GP", "GP", "GP", "GP", "GU", "GU", "GU", 
"GU", "GU", "GU", "GU", "GU", "GU", "GU", "GU", "GU", "GU", "GU", 
"GU", "GU", "GT", "GT", "GT", "GT", "GT", "GT", "GT", "GT", "GT", 
"GT", "GT", "GT", "GT", "GT", "GT", "GT", "GT", "GT", "GT", "GT", 
"GT", "GT", "GT", "GT", "GT", "GT", "GT", "GT", "GT", "GT", "GT", 
"GT", "GT", "GN", "GN", "GN", "GN", "GN", "GN", "GN", "GN", "GN", 
"GN", "GN", "GN", "GN", "GN", "GN", "GN", "GN", "GN", "GN", "GN", 
"GN", "GN", "GN", "GN", "GN", "GN", "GN", "GN", "GN", "GN", "GN", 
"GN", "GN", "GN", "GN", "GN", "GN", "GW", "GW", "GW", "GW", "GW", 
"GW", "GW", "GW", "GW", "GW", "GW", "GW", "GW", "GW", "GW", "GW", 
"GW", "GW", "GW", "GW", "GW", "GW", "GW", "GW", "GW", "GW", "GW", 
"GW", "GW", "GW", "GW", "GW", "GY", "GY", "GY", "GY", "GY", "GY", 
"GY", "GY", "GY", "GY", "GY", "GY", "GY", "GY", "GY", "GY", "GY", 
"GY", "GY", "GY", "GY", "GY", "GY", "GY", "GY", "GY", "GY", "GY", 
"GY", "HT", "HT", "HT", "HT", "HT", "HT", "HT", "HT", "HT", "HT", 
"HT", "HT", "HT", "HT", "HT", "HT", "HT", "HT", "HT", "HT", "HT", 
"HT", "HT", "HT", "HT", "HT", "HT", "HT", "HT", "HT", "VA", "VA", 
"VA", "VA", "VA", "VA", "VA", "VA", "HN", "HN", "HN", "HN", "HN", 
"HN", "HN", "HN", "HN", "HN", "HN", "HN", "HN", "HN", "HN", "HN", 
"HN", "HN", "HN", "HN", "HN", "HN", "HN", "HN", "HN", "HN", "HN", 
"HN", "HN", "HN", "HN", "HN", "HN", "HU", "HU", "HU", "HU", "HU", 
"HU", "HU", "HU", "HU", "HU", "HU", "HU", "HU", "HU", "HU", "HU", 
"HU", "HU", "HU", "HU", "HU", "HU", "HU", "HU", "HU", "HU", "HU", 
"HU", "HU", "HU", "HU", "HU", "HU", "HU", "HU", "HU", "IS", "IS", 
"IS", "IS", "IS", "IS", "IS", "IS", "IS", "IS", "IS", "IS", "IS", 
"IS", "IS", "IS", "IS", "IS", "IS", "IS", "IS", "IS", "IS", "IS", 
"IS", "IS", "IS", "IS", "IS", "IS", "IS", "IS", "IS", "IS", "IS", 
"IS", "IN", "IN", "IN", "IN", "IN", "IN", "IN", "IN", "IN", "IN", 
"IN", "IN", "IN", "IN", "IN", "IN", "IN", "IN", "IN", "IN", "IN", 
"IN", "IN", "IN", "IN", "IN", "IN", "IN", "IN", "IN", "IN", "IN", 
"IN", "IN", "ID", "ID", "ID", "ID", "ID", "ID", "ID", "ID", "ID", 
"ID", "ID", "ID", "ID", "ID", "ID", "ID", "ID", "ID", "ID", "ID", 
"ID", "ID", "ID", "ID", "ID", "ID", "ID", "ID", "ID", "ID", "ID", 
"ID", "ID", "ID", "IR", "IR", "IR", "IR", "IR", "IR", "IR", "IR", 
"IR", "IR", "IR", "IR", "IR", "IR", "IR", "IR", "IR", "IR", "IR", 
"IR", "IR", "IR", "IR", "IR", "IR", "IR", "IR", "IR", "IR", "IR", 
"IR", "IR", "IR", "IR", "IR", "IR", "IQ", "IQ", "IQ", "IQ", "IQ", 
"IQ", "IQ", "IQ", "IQ", "IQ", "IQ", "IQ", "IQ", "IQ", "IQ", "IQ", 
"IQ", "IQ", "IQ", "IQ", "IQ", "IQ", "IQ", "IQ", "IQ", "IQ", "IQ", 
"IQ", "IQ", "IQ", "IQ", "IQ", "IQ", "IQ", "IQ", "IQ", "IE", "IE", 
"IE", "IE", "IE", "IE", "IE", "IE", "IE", "IE", "IE", "IE", "IE", 
"IE", "IE", "IE", "IE", "IE", "IE", "IE", "IE", "IE", "IE", "IE", 
"IE", "IE", "IE", "IE", "IE", "IE", "IE", "IE", "IE", "IE", "IE", 
"IE", "IM", "IM", "IM", "IM", "IM", "IM", "IM", "IM", "IL", "IL", 
"IL", "IL", "IL", "IL", "IL", "IL", "IL", "IL", "IL", "IL", "IL", 
"IL", "IL", "IL", "IL", "IL", "IL", "IL", "IL", "IL", "IL", "IL", 
"IL", "IL", "IL", "IL", "IL", "IL", "IL", "IL", "IL", "IL", "IL", 
"IT", "IT", "IT", "IT", "IT", "IT", "IT", "IT", "IT", "IT", "IT", 
"IT", "IT", "IT", "IT", "IT", "IT", "IT", "IT", "IT", "IT", "IT", 
"IT", "IT", "IT", "IT", "IT", "IT", "IT", "IT", "IT", "IT", "IT", 
"IT", "IT", "JM", "JM", "JM", "JM", "JM", "JM", "JM", "JM", "JM", 
"JM", "JM", "JM", "JM", "JM", "JM", "JM", "JM", "JM", "JM", "JM", 
"JM", "JM", "JM", "JM", "JM", "JM", "JM", "JM", "JM", "JP", "JP", 
"JP", "JP", "JP", "JP", "JP", "JP", "JP", "JP", "JP", "JP", "JP", 
"JP", "JP", "JP", "JP", "JP", "JP", "JP", "JP", "JP", "JP", "JP", 
"JP", "JP", "JP", "JP", "JP", "JP", "JP", "JP", "JP", "JP", "JP", 
"JP", "JO", "JO", "JO", "JO", "JO", "JO", "JO", "JO", "JO", "JO", 
"JO", "JO", "JO", "JO", "JO", "JO", "JO", "JO", "JO", "JO", "JO", 
"JO", "JO", "JO", "JO", "JO", "JO", "JO", "JO", "JO", "JO", "JO", 
"JO", "JO", "JO", "KZ", "KZ", "KZ", "KZ", "KZ", "KZ", "KZ", "KZ", 
"KZ", "KZ", "KZ", "KZ", "KZ", "KZ", "KZ", "KZ", "KZ", "KZ", "KZ", 
"KZ", "KZ", "KZ", "KZ", "KZ", "KZ", "KZ", "KZ", "KZ", "KZ", "KZ", 
"KZ", "KZ", "KZ", "KZ", "KZ", "KZ", "KE", "KE", "KE", "KE", "KE", 
"KE", "KE", "KE", "KE", "KE", "KE", "KE", "KE", "KE", "KE", "KE", 
"KE", "KE", "KE", "KE", "KE", "KE", "KE", "KE", "KE", "KE", "KE", 
"KE", "KE", "KE", "KE", "KE", "KE", "KE", "KE", "KE", "KI", "KI", 
"KI", "KI", "KI", "KI", "KI", "KI", "KI", "KI", "KI", "KI", "KI", 
"KI", "KI", "KI", "KW", "KW", "KW", "KW", "KW", "KW", "KW", "KW", 
"KW", "KW", "KW", "KW", "KW", "KW", "KW", "KW", "KW", "KW", "KW", 
"KW", "KW", "KW", "KW", "KW", "KW", "KW", "KW", "KW", "KW", "KW", 
"KW", "KW", "KW", "KW", "KW", "KW", "KG", "KG", "KG", "KG", "KG", 
"KG", "KG", "KG", "KG", "KG", "KG", "KG", "KG", "KG", "KG", "KG", 
"KG", "KG", "KG", "KG", "KG", "KG", "KG", "KG", "KG", "KG", "KG", 
"KG", "KG", "KG", "KG", "KG", "KG", "KG", "KG", "KG", "LA", "LA", 
"LA", "LA", "LA", "LA", "LA", "LA", "LA", "LA", "LA", "LA", "LA", 
"LA", "LA", "LA", "LA", "LA", "LA", "LV", "LV", "LV", "LV", "LV", 
"LV", "LV", "LV", "LV", "LV", "LV", "LV", "LV", "LV", "LV", "LV", 
"LV", "LV", "LV", "LV", "LV", "LV", "LV", "LV", "LV", "LV", "LV", 
"LV", "LV", "LV", "LV", "LV", "LV", "LV", "LV", "LV", "LB", "LB", 
"LB", "LB", "LB", "LB", "LB", "LB", "LB", "LB", "LB", "LB", "LB", 
"LB", "LB", "LB", "LB", "LB", "LB", "LB", "LB", "LB", "LB", "LB", 
"LB", "LB", "LB", "LB", "LB", "LB", "LB", "LB", "LB", "LB", "LB", 
"LB", "LS", "LS", "LS", "LS", "LS", "LS", "LS", "LS", "LS", "LS", 
"LS", "LS", "LS", "LS", "LS", "LS", "LS", "LS", "LS", "LS", "LS", 
"LS", "LS", "LS", "LS", "LS", "LR", "LR", "LR", "LR", "LR", "LR", 
"LR", "LR", "LR", "LR", "LR", "LR", "LR", "LR", "LR", "LR", "LR", 
"LR", "LR", "LR", "LR", "LR", "LR", "LR", "LR", "LR", "LR", "LR", 
"LR", "LR", "LR", "LR", "LR", "LR", "LR", "LY", "LY", "LY", "LY", 
"LY", "LY", "LY", "LY", "LY", "LY", "LY", "LY", "LY", "LY", "LY", 
"LY", "LY", "LY", "LY", "LY", "LY", "LY", "LY", "LY", "LY", "LY", 
"LY", "LY", "LY", "LY", "LY", "LY", "LY", "LY", "LY", "LY", "LI", 
"LI", "LI", "LI", "LI", "LI", "LI", "LI", "LI", "LI", "LI", "LI", 
"LI", "LI", "LI", "LI", "LI", "LI", "LI", "LI", "LI", "LI", "LI", 
"LI", "LI", "LT", "LT", "LT", "LT", "LT", "LT", "LT", "LT", "LT", 
"LT", "LT", "LT", "LT", "LT", "LT", "LT", "LT", "LT", "LT", "LT", 
"LT", "LT", "LT", "LT", "LT", "LT", "LT", "LT", "LT", "LT", "LT", 
"LT", "LT", "LT", "LT", "LT", "LU", "LU", "LU", "LU", "LU", "LU", 
"LU", "LU", "LU", "LU", "LU", "LU", "LU", "LU", "LU", "LU", "LU", 
"LU", "LU", "LU", "LU", "LU", "LU", "LU", "LU", "LU", "LU", "LU", 
"LU", "LU", "LU", "LU", "LU", "LU", "LU", "MG", "MG", "MG", "MG", 
"MG", "MG", "MG", "MG", "MG", "MG", "MG", "MG", "MG", "MG", "MG", 
"MG", "MG", "MG", "MG", "MG", "MG", "MG", "MG", "MG", "MG", "MG", 
"MG", "MG", "MW", "MW", "MW", "MW", "MW", "MW", "MW", "MW", "MW", 
"MW", "MW", "MW", "MW", "MW", "MW", "MW", "MW", "MW", "MW", "MW", 
"MW", "MW", "MW", "MW", "MW", "MW", "MW", "MW", "MW", "MW", "MW", 
"MW", "MW", "MW", "MW", "MY", "MY", "MY", "MY", "MY", "MY", "MY", 
"MY", "MY", "MY", "MY", "MY", "MY", "MY", "MY", "MY", "MY", "MY", 
"MY", "MY", "MY", "MY", "MY", "MY", "MY", "MY", "MY", "MY", "MY", 
"MY", "MY", "MY", "MY", "MY", "MY", "MY", "MV", "MV", "MV", "MV", 
"MV", "MV", "MV", "MV", "MV", "MV", "MV", "MV", "MV", "MV", "MV", 
"MV", "ML", "ML", "ML", "ML", "ML", "ML", "ML", "ML", "ML", "ML", 
"ML", "ML", "ML", "ML", "ML", "ML", "ML", "ML", "ML", "ML", "ML", 
"ML", "ML", "ML", "ML", "ML", "ML", "ML", "ML", "ML", "ML", "ML", 
"ML", "ML", "MT", "MT", "MT", "MT", "MT", "MT", "MT", "MT", "MT", 
"MT", "MT", "MT", "MT", "MT", "MT", "MT", "MT", "MT", "MT", "MT", 
"MT", "MT", "MT", "MT", "MT", "MT", "MT", "MT", "MT", "MT", "MT", 
"MT", "MH", "MH", "MH", "MH", "MH", "MH", "MH", "MH", "MQ", "MQ", 
"MQ", "MQ", "MQ", "MQ", "MQ", "MQ", "MQ", "MQ", "MQ", "MQ", "MQ", 
"MQ", "MQ", "MQ", "MR", "MR", "MR", "MR", "MR", "MR", "MR", "MR", 
"MR", "MR", "MR", "MR", "MR", "MR", "MR", "MR", "MR", "MR", "MR", 
"MR", "MR", "MR", "MR", "MR", "MR", "MR", "MR", "MR", "MR", "MR", 
"MR", "MR", "MR", "MU", "MU", "MU", "MU", "MU", "MU", "MU", "MU", 
"MU", "MU", "MU", "MU", "MU", "MU", "MU", "MU", "MU", "MU", "MU", 
"MU", "MU", "YT", "YT", "YT", "YT", "YT", "YT", "YT", "YT", "YT", 
"YT", "YT", "YT", "YT", "YT", "YT", "YT", "MX", "MX", "MX", "MX", 
"MX", "MX", "MX", "MX", "MX", "MX", "MX", "MX", "MX", "MX", "MX", 
"MX", "MX", "MX", "MX", "MX", "MX", "MX", "MX", "MX", "MX", "MX", 
"MX", "MX", "MX", "MX", "MX", "MX", "MX", "MX", "FM", "FM", "FM", 
"FM", "FM", "FM", "FM", "FM", "FM", "FM", "FM", "FM", "FM", "FM", 
"FM", "FM", "FM", "FM", "FM", "FM", "FM", "FM", "FM", "MC", "MC", 
"MC", "MC", "MC", "MC", "MC", "MC", "MC", "MC", "MC", "MC", "MC", 
"MC", "MC", "MC", "MN", "MN", "MN", "MN", "MN", "MN", "MN", "MN", 
"MN", "MN", "MN", "MN", "MN", "MN", "MN", "MN", "MN", "MN", "MN", 
"MN", "MN", "MN", "MN", "MN", "MN", "MN", "MN", "MN", "MN", "MN", 
"MN", "MN", "MN", "MN", "MN", "ME", "ME", "ME", "ME", "ME", "ME", 
"ME", "ME", "ME", "ME", "ME", "ME", "ME", "ME", "ME", "ME", "ME", 
"ME", "ME", "ME", "ME", "ME", "ME", "ME", "ME", "ME", "ME", "ME", 
"MS", "MS", "MS", "MS", "MS", "MS", "MS", "MS", "MS", "MS", "MA", 
"MA", "MA", "MA", "MA", "MA", "MA", "MA", "MA", "MA", "MA", "MA", 
"MA", "MA", "MA", "MA", "MA", "MA", "MA", "MA", "MA", "MA", "MA", 
"MA", "MA", "MA", "MA", "MA", "MA", "MA", "MA", "MA", "MZ", "MZ", 
"MZ", "MZ", "MZ", "MZ", "MZ", "MZ", "MZ", "MZ", "MZ", "MZ", "MZ", 
"MZ", "MZ", "MZ", "MZ", "MZ", "MZ", "MZ", "MZ", "MZ", "MZ", "MZ", 
"MZ", "MZ", "MZ", "MZ", "MZ", "MZ", "MZ", "MZ", "MZ", "MZ", "MZ", 
"MZ", "MM", "MM", "MM", "MM", "MM", "MM", "MM", "MM", "MM", "MM", 
"MM", "MM", "MM", "MM", "MM", "MM", "MM", "MM", "MM", "MM", "MM", 
"MM", "MM", "MM", "MM", "MM", "MM", "MM", "MM", "NA", "NA", "NA", 
"NA", "NA", "NA", "NA", "NA", "NA", "NA", "NA", "NA", "NA", "NA", 
"NA", "NA", "NA", "NA", "NA", "NA", "NA", "NA", "NA", "NA", "NA", 
"NA", "NA", "NA", "NA", "NA", "NA", "NA", "NA", "NA", "NA", "NA", 
"NR", "NR", "NR", "NR", "NR", "NR", "NR", "NR", "NR", "NR", "NR", 
"NR", "NR", "NR", "NR", "NR", "NR", "NR", "NP", "NP", "NP", "NP", 
"NP", "NP", "NP", "NP", "NP", "NP", "NP", "NP", "NP", "NP", "NP", 
"NP", "NP", "NP", "NP", "NP", "NP", "NP", "NP", "NP", "NP", "NP", 
"NP", "NP", "NP", "NP", "NP", "NP", "NP", "NP", "NP", "NP", "NL", 
"NL", "NL", "NL", "NL", "NL", "NL", "NL", "NL", "NL", "NL", "NL", 
"NL", "NL", "NL", "NL", "NL", "NL", "NL", "NL", "NL", "NL", "NL", 
"NL", "NL", "NL", "NL", "NL", "NL", "NL", "NL", "NL", "NL", "NL", 
"NL", "NL", "NC", "NC", "NC", "NC", "NC", "NC", "NC", "NC", "NC", 
"NC", "NC", "NC", "NC", "NC", "NC", "NC", "NZ", "NZ", "NZ", "NZ", 
"NZ", "NZ", "NZ", "NZ", "NZ", "NZ", "NZ", "NZ", "NZ", "NZ", "NZ", 
"NZ", "NZ", "NZ", "NZ", "NZ", "NZ", "NZ", "NZ", "NZ", "NZ", "NZ", 
"NZ", "NZ", "NZ", "NZ", "NZ", "NZ", "NZ", "NZ", "NI", "NI", "NI", 
"NI", "NI", "NI", "NI", "NI", "NI", "NI", "NI", "NI", "NI", "NI", 
"NI", "NI", "NI", "NI", "NI", "NI", "NI", "NI", "NI", "NI", "NI", 
"NI", "NI", "NI", "NI", "NI", "NI", "NI", "NI", "NI", "NE", "NE", 
"NE", "NE", "NE", "NE", "NE", "NE", "NE", "NE", "NE", "NE", "NE", 
"NE", "NE", "NE", "NE", "NE", "NE", "NE", "NE", "NE", "NE", "NE", 
"NE", "NE", "NE", "NE", "NE", "NE", "NE", "NE", "NE", "NE", "NE", 
"NE", "NG", "NG", "NG", "NG", "NG", "NG", "NG", "NG", "NG", "NG", 
"NG", "NG", "NG", "NG", "NG", "NG", "NG", "NG", "NG", "NG", "NG", 
"NG", "NG", "NG", "NG", "NG", "NG", "NG", "NG", "NG", "NG", "NG", 
"NG", "NG", "NG", "NG", "NU", "NU", "NU", "NU", "NU", "NU", "NU", 
"NU", "MK", "MK", "MK", "MK", "MK", "MK", "MK", "MK", "MK", "MK", 
"MK", "MK", "MK", "MK", "MK", "MK", "MK", "MK", "MK", "MK", "MK", 
"MK", "MK", "MK", "MK", "MK", "MK", "MK", "MK", "MK", "MK", "MK", 
"MK", "MK", "MK", "MK", "MP", "MP", "MP", "MP", "MP", "MP", "MP", 
"MP", "NO", "NO", "NO", "NO", "NO", "NO", "NO", "NO", "NO", "NO", 
"NO", "NO", "NO", "NO", "NO", "NO", "NO", "NO", "NO", "NO", "NO", 
"NO", "NO", "NO", "NO", "NO", "NO", "NO", "NO", "NO", "NO", "NO", 
"NO", "NO", "NO", "OM", "OM", "OM", "OM", "OM", "OM", "OM", "OM", 
"OM", "OM", "OM", "OM", "OM", "OM", "OM", "OM", "OM", "OM", "OM", 
"OM", "OM", "OM", "OM", "OM", "OM", "OM", "OM", "OM", "OM", "OM", 
"OM", "PK", "PK", "PK", "PK", "PK", "PK", "PK", "PK", "PK", "PK", 
"PK", "PK", "PK", "PK", "PK", "PK", "PK", "PK", "PK", "PK", "PK", 
"PK", "PK", "PK", "PK", "PK", "PK", "PK", "PK", "PK", "PK", "PK", 
"PK", "PK", "PK", "PK", "PW", "PW", "PW", "PW", "PW", "PW", "PW", 
"PW", "PW", "PW", "PW", "PW", "PW", "PW", "PA", "PA", "PA", "PA", 
"PA", "PA", "PA", "PA", "PA", "PA", "PA", "PA", "PA", "PA", "PA", 
"PA", "PA", "PA", "PA", "PA", "PA", "PA", "PA", "PA", "PA", "PA", 
"PA", "PA", "PA", "PA", "PA", "PA", "PA", "PA", "PA", "PA", "PG", 
"PG", "PG", "PG", "PG", "PG", "PG", "PG", "PG", "PG", "PG", "PG", 
"PG", "PG", "PG", "PG", "PG", "PG", "PG", "PG", "PG", "PG", "PG", 
"PG", "PG", "PG", "PG", "PG", "PG", "PG", "PG", "PG", "PG", "PY", 
"PY", "PY", "PY", "PY", "PY", "PY", "PY", "PY", "PY", "PY", "PY", 
"PY", "PY", "PY", "PY", "PY", "PY", "PY", "PY", "PY", "PY", "PY", 
"PY", "PY", "PY", "PY", "PY", "PY", "PY", "PY", "PY", "PY", "PE", 
"PE", "PE", "PE", "PE", "PE", "PE", "PE", "PE", "PE", "PE", "PE", 
"PE", "PE", "PE", "PE", "PE", "PE", "PE", "PE", "PE", "PE", "PE", 
"PE", "PE", "PE", "PE", "PE", "PE", "PE", "PE", "PE", "PE", "PE", 
"PE", "PH", "PH", "PH", "PH", "PH", "PH", "PH", "PH", "PH", "PH", 
"PH", "PH", "PH", "PH", "PH", "PH", "PH", "PH", "PH", "PH", "PH", 
"PH", "PH", "PH", "PH", "PH", "PH", "PH", "PH", "PH", "PH", "PH", 
"PH", "PH", "PH", "PH", "PL", "PL", "PL", "PL", "PL", "PL", "PL", 
"PL", "PL", "PL", "PL", "PL", "PL", "PL", "PL", "PL", "PL", "PL", 
"PL", "PL", "PL", "PL", "PL", "PL", "PL", "PL", "PL", "PL", "PL", 
"PL", "PL", "PL", "PL", "PL", "PL", "PL", "PT", "PT", "PT", "PT", 
"PT", "PT", "PT", "PT", "PT", "PT", "PT", "PT", "PT", "PT", "PT", 
"PT", "PT", "PT", "PT", "PT", "PT", "PT", "PT", "PT", "PT", "PT", 
"PT", "PT", "PT", "PT", "PT", "PT", "PT", "PT", "PR", "PR", "PR", 
"PR", "PR", "PR", "PR", "PR", "PR", "PR", "PR", "PR", "PR", "PR", 
"PR", "PR", "QA", "QA", "QA", "QA", "QA", "QA", "QA", "QA", "QA", 
"QA", "QA", "QA", "QA", "QA", "QA", "QA", "QA", "QA", "QA", "QA", 
"QA", "QA", "QA", "QA", "QA", "QA", "QA", "QA", "QA", "QA", "QA", 
"QA", "QA", "QA", "QA", "KR", "KR", "KR", "KR", "KR", "KR", "KR", 
"KR", "KR", "KR", "KR", "KR", "KR", "KR", "KR", "KR", "KR", "KR", 
"KR", "KR", "KR", "KR", "KR", "KR", "KR", "KR", "KR", "KR", "KR", 
"KR", "KR", "KR", "KR", "KR", "KR", "MD", "MD", "MD", "MD", "MD", 
"MD", "MD", "MD", "MD", "MD", "MD", "MD", "MD", "MD", "MD", "MD", 
"MD", "MD", "MD", "MD", "MD", "MD", "MD", "MD", "MD", "MD", "MD", 
"MD", "MD", "MD", "MD", "MD", "MD", "MD", "MD", "MD", "RE", "RE", 
"RE", "RE", "RE", "RE", "RE", "RE", "RE", "RE", "RE", "RE", "RE", 
"RE", "RE", "RE", "RO", "RO", "RO", "RO", "RO", "RO", "RO", "RO", 
"RO", "RO", "RO", "RO", "RO", "RO", "RO", "RO", "RO", "RO", "RO", 
"RO", "RO", "RO", "RO", "RO", "RO", "RO", "RO", "RO", "RO", "RO", 
"RO", "RO", "RO", "RO", "RO", "RO", "RU", "RU", "RU", "RU", "RU", 
"RU", "RU", "RU", "RU", "RU", "RU", "RU", "RU", "RU", "RU", "RU", 
"RU", "RU", "RU", "RU", "RU", "RU", "RU", "RU", "RU", "RU", "RU", 
"RU", "RU", "RU", "RU", "RU", "RU", "RU", "RU", "RU", "RW", "RW", 
"RW", "RW", "RW", "RW", "RW", "RW", "RW", "RW", "RW", "RW", "RW", 
"RW", "RW", "RW", "RW", "RW", "RW", "RW", "RW", "RW", "RW", "RW", 
"RW", "RW", "RW", "RW", "RW", "RW", "RW", "RW", "RW", "RW", "RW", 
"RW", "SH", "SH", "SH", "SH", "SH", "SH", "SH", "SH", "KN", "KN", 
"KN", "KN", "KN", "KN", "KN", "KN", "KN", "KN", "KN", "KN", "KN", 
"KN", "LC", "LC", "LC", "LC", "LC", "LC", "LC", "LC", "LC", "LC", 
"LC", "LC", "LC", "LC", "LC", "LC", "LC", "LC", "LC", "LC", "LC", 
"LC", "LC", "LC", "LC", "LC", "PM", "PM", "PM", "PM", "PM", "PM", 
"PM", "PM", "VC", "VC", "VC", "VC", "VC", "VC", "VC", "VC", "VC", 
"VC", "VC", "VC", "VC", "VC", "VC", "VC", "VC", "VC", "VC", "VC", 
"WS", "WS", "WS", "WS", "WS", "WS", "WS", "WS", "WS", "WS", "WS", 
"WS", "WS", "WS", "WS", "WS", "WS", "WS", "WS", "WS", "SM", "SM", 
"SM", "SM", "SM", "SM", "SM", "SM", "ST", "ST", "ST", "ST", "ST", 
"ST", "ST", "ST", "ST", "ST", "ST", "ST", "ST", "ST", "ST", "ST", 
"SA", "SA", "SA", "SA", "SA", "SA", "SA", "SA", "SA", "SA", "SA", 
"SA", "SA", "SA", "SA", "SA", "SA", "SA", "SA", "SA", "SA", "SA", 
"SA", "SA", "SA", "SA", "SA", "SA", "SA", "SA", "SA", "SA", "SA", 
"SA", "SA", "SA", "SN", "SN", "SN", "SN", "SN", "SN", "SN", "SN", 
"SN", "SN", "SN", "SN", "SN", "SN", "SN", "SN", "SN", "SN", "SN", 
"SN", "SN", "SN", "SN", "SN", "SN", "SN", "SN", "SN", "SN", "SN", 
"SN", "SN", "SN", "SN", "SN", "SN", "SN", "RS", "RS", "RS", "RS", 
"RS", "RS", "RS", "RS", "RS", "RS", "RS", "RS", "RS", "RS", "RS", 
"RS", "RS", "RS", "RS", "RS", "RS", "RS", "RS", "RS", "RS", "RS", 
"RS", "RS", "RS", "RS", "RS", "RS", "RS", "RS", "RS", "RS", "SC", 
"SC", "SC", "SC", "SC", "SC", "SC", "SC", "SC", "SC", "SC", "SC", 
"SC", "SC", "SC", "SC", "SC", "SC", "SL", "SL", "SL", "SL", "SL", 
"SL", "SL", "SL", "SL", "SL", "SL", "SL", "SL", "SL", "SL", "SL", 
"SL", "SL", "SL", "SL", "SL", "SL", "SL", "SL", "SL", "SL", "SL", 
"SL", "SL", "SL", "SL", "SL", "SL", "SL", "SL", "SG", "SG", "SG", 
"SG", "SG", "SG", "SG", "SG", "SG", "SG", "SG", "SG", "SG", "SG", 
"SG", "SG", "SG", "SG", "SG", "SG", "SG", "SG", "SG", "SG", "SG", 
"SG", "SG", "SG", "SX", "SX", "SX", "SX", "SX", "SX", "SX", "SX", 
"SX", "SX", "SX", "SX", "SX", "SX", "SX", "SX", "SX", "SX", "SX", 
"SX", "SK", "SK", "SK", "SK", "SK", "SK", "SK", "SK", "SK", "SK", 
"SK", "SK", "SK", "SK", "SK", "SK", "SK", "SK", "SK", "SK", "SK", 
"SK", "SK", "SK", "SK", "SK", "SK", "SK", "SK", "SK", "SK", "SK", 
"SK", "SK", "SK", "SI", "SI", "SI", "SI", "SI", "SI", "SI", "SI", 
"SI", "SI", "SI", "SI", "SI", "SI", "SI", "SI", "SI", "SI", "SI", 
"SI", "SI", "SI", "SI", "SI", "SI", "SI", "SI", "SI", "SI", "SI", 
"SI", "SI", "SI", "SI", "SI", "SI", "SI", "SI", "SI", "SB", "SB", 
"SB", "SB", "SB", "SB", "SB", "SB", "SB", "SB", "SB", "SB", "SB", 
"SB", "SB", "SB", "SB", "SB", "SB", "SB", "SB", "SB", "SO", "SO", 
"SO", "SO", "SO", "SO", "SO", "SO", "SO", "SO", "SO", "SO", "SO", 
"SO", "SO", "SO", "SO", "SO", "SO", "SO", "SO", "SO", "SO", "SO", 
"SO", "SO", "SO", "SO", "SO", "SO", "SO", "SO", "SO", "SO", "SO", 
"SO", "ZA", "ZA", "ZA", "ZA", "ZA", "ZA", "ZA", "ZA", "ZA", "ZA", 
"ZA", "ZA", "ZA", "ZA", "ZA", "ZA", "ZA", "ZA", "ZA", "ZA", "ZA", 
"ZA", "ZA", "ZA", "ZA", "ZA", "ZA", "ZA", "ZA", "ZA", "ZA", "ZA", 
"ZA", "SS", "SS", "SS", "SS", "SS", "SS", "SS", "SS", "SS", "SS", 
"SS", "SS", "SS", "SS", "SS", "SS", "SS", "SS", "SS", "SS", "SS", 
"SS", "SS", "SS", "ES", "ES", "ES", "ES", "ES", "ES", "ES", "ES", 
"ES", "ES", "ES", "ES", "ES", "ES", "ES", "ES", "ES", "ES", "ES", 
"ES", "ES", "ES", "ES", "ES", "ES", "ES", "ES", "ES", "ES", "ES", 
"ES", "ES", "ES", "ES", "ES", "LK", "LK", "LK", "LK", "LK", "LK", 
"LK", "LK", "LK", "LK", "LK", "LK", "LK", "LK", "LK", "LK", "LK", 
"LK", "LK", "LK", "LK", "LK", "LK", "LK", "LK", "LK", "LK", "LK", 
"LK", "LK", "LK", "LK", "LK", "LK", "LK", "LK", "PS", "PS", "PS", 
"PS", "PS", "PS", "PS", "PS", "PS", "PS", "PS", "PS", "PS", "PS", 
"PS", "PS", "PS", "PS", "SD", "SD", "SD", "SD", "SD", "SD", "SD", 
"SD", "SD", "SD", "SD", "SD", "SD", "SD", "SD", "SD", "SD", "SD", 
"SD", "SD", "SD", "SD", "SD", "SD", "SD", "SD", "SD", "SD", "SD", 
"SD", "SD", "SD", "SD", "SD", "SD", "SD", "SR", "SR", "SR", "SR", 
"SR", "SR", "SR", "SR", "SR", "SR", "SR", "SR", "SR", "SR", "SR", 
"SR", "SR", "SR", "SR", "SR", "SR", "SR", "SR", "SR", "SR", "SR", 
"SR", "SR", "SR", "SR", "SR", "SE", "SE", "SE", "SE", "SE", "SE", 
"SE", "SE", "SE", "SE", "SE", "SE", "SE", "SE", "SE", "SE", "SE", 
"SE", "SE", "SE", "SE", "SE", "SE", "SE", "SE", "SE", "SE", "SE", 
"SE", "SE", "SE", "SE", "SE", "SE", "SE", "SE", "CH", "CH", "CH", 
"CH", "CH", "CH", "CH", "CH", "CH", "CH", "CH", "CH", "CH", "CH", 
"CH", "CH", "CH", "CH", "CH", "CH", "CH", "CH", "CH", "CH", "CH", 
"CH", "CH", "CH", "CH", "CH", "CH", "CH", "CH", "CH", "CH", "SY", 
"SY", "SY", "SY", "SY", "SY", "SY", "SY", "SY", "SY", "SY", "SY", 
"SY", "SY", "SY", "SY", "SY", "SY", "SY", "SY", "SY", "SY", "SY", 
"SY", "SY", "SY", "SY", "SY", "SY", "SY", "SY", "SY", "SY", "SY", 
"SY", "SY", "TJ", "TJ", "TJ", "TJ", "TJ", "TJ", "TJ", "TJ", "TJ", 
"TJ", "TJ", "TJ", "TJ", "TJ", "TJ", "TJ", "TJ", "TJ", "TJ", "TJ", 
"TJ", "TJ", "TJ", "TJ", "TJ", "TJ", "TJ", "TJ", "TJ", "TJ", "TJ", 
"TJ", "TJ", "TJ", "TJ", "TJ", "TH", "TH", "TH", "TH", "TH", "TH", 
"TH", "TH", "TH", "TH", "TH", "TH", "TH", "TH", "TH", "TH", "TH", 
"TH", "TH", "TH", "TH", "TH", "TH", "TH", "TH", "TH", "TH", "TH", 
"TH", "TH", "TH", "TH", "TH", "TH", "TH", "TH", "TL", "TL", "TL", 
"TL", "TL", "TL", "TL", "TL", "TL", "TL", "TL", "TL", "TL", "TL", 
"TL", "TL", "TL", "TL", "TL", "TL", "TL", "TL", "TL", "TL", "TL", 
"TL", "TG", "TG", "TG", "TG", "TG", "TG", "TG", "TG", "TG", "TG", 
"TG", "TG", "TG", "TG", "TG", "TG", "TG", "TG", "TG", "TG", "TG", 
"TG", "TG", "TG", "TG", "TG", "TG", "TG", "TG", "TG", "TG", "TG", 
"TG", "TG", "TG", "TG", "TG", "TK", "TK", "TK", "TK", "TK", "TK", 
"TK", "TK", "TO", "TO", "TO", "TO", "TO", "TO", "TO", "TO", "TO", 
"TO", "TO", "TO", "TO", "TO", "TO", "TO", "TO", "TO", "TO", "TO", 
"TT", "TT", "TT", "TT", "TT", "TT", "TT", "TT", "TT", "TT", "TT", 
"TT", "TT", "TT", "TT", "TT", "TT", "TT", "TT", "TT", "TT", "TT", 
"TT", "TT", "TT", "TT", "TT", "TT", "TT", "TT", "TN", "TN", "TN", 
"TN", "TN", "TN", "TN", "TN", "TN", "TN", "TN", "TN", "TN", "TN", 
"TN", "TN", "TN", "TN", "TN", "TN", "TN", "TN", "TN", "TN", "TN", 
"TN", "TN", "TN", "TN", "TN", "TN", "TN", "TN", "TN", "TN", "TR", 
"TR", "TR", "TR", "TR", "TR", "TR", "TR", "TR", "TR", "TR", "TR", 
"TR", "TR", "TR", "TR", "TR", "TR", "TR", "TR", "TR", "TR", "TR", 
"TR", "TR", "TR", "TR", "TR", "TR", "TR", "TR", "TR", "TR", "TR", 
"TR", "TR", "TM", "TM", "TM", "TM", "TM", "TM", "TM", "TM", "TM", 
"TM", "TM", "TM", "TM", "TM", "TM", "TM", "TM", "TM", "TM", "TM", 
"TM", "TM", "TM", "TM", "TM", "TM", "TM", "TM", "TM", "TM", "TM", 
"TM", "TC", "TC", "TC", "TC", "TC", "TC", "TC", "TC", "TC", "TC", 
"TC", "TC", "TC", "TC", "TC", "TC", "TC", "TC", "TC", "TV", "TV", 
"TV", "TV", "TV", "TV", "TV", "TV", "UG", "UG", "UG", "UG", "UG", 
"UG", "UG", "UG", "UG", "UG", "UG", "UG", "UG", "UG", "UG", "UG", 
"UG", "UG", "UG", "UG", "UG", "UG", "UG", "UG", "UG", "UG", "UG", 
"UG", "UG", "UG", "UG", "UG", "UG", "UG", "UG", "UG", "UA", "UA", 
"UA", "UA", "UA", "UA", "UA", "UA", "UA", "UA", "UA", "UA", "UA", 
"UA", "UA", "UA", "UA", "UA", "UA", "UA", "UA", "UA", "UA", "UA", 
"UA", "UA", "UA", "UA", "UA", "UA", "UA", "UA", "UA", "UA", "UA", 
"UA", "AE", "AE", "AE", "AE", "AE", "AE", "AE", "AE", "AE", "AE", 
"AE", "AE", "AE", "AE", "AE", "AE", "AE", "AE", "AE", "AE", "AE", 
"AE", "AE", "AE", "AE", "AE", "AE", "AE", "AE", "AE", "AE", "AE", 
"AE", "GB", "GB", "GB", "GB", "GB", "GB", "GB", "GB", "GB", "GB", 
"GB", "GB", "GB", "GB", "GB", "GB", "GB", "GB", "GB", "GB", "GB", 
"GB", "GB", "GB", "GB", "GB", "GB", "GB", "GB", "GB", "GB", "GB", 
"GB", "GB", "GB", "GB", "TZ", "TZ", "TZ", "TZ", "TZ", "TZ", "TZ", 
"TZ", "TZ", "TZ", "TZ", "TZ", "TZ", "TZ", "TZ", "TZ", "TZ", "TZ", 
"TZ", "TZ", "TZ", "TZ", "TZ", "TZ", "TZ", "TZ", "TZ", "TZ", "TZ", 
"TZ", "TZ", "TZ", "TZ", "TZ", "TZ", "TZ", "US", "US", "US", "US", 
"US", "US", "US", "US", "US", "US", "US", "US", "US", "US", "US", 
"US", "US", "US", "US", "US", "US", "US", "US", "US", "US", "US", 
"US", "US", "US", "US", "US", "US", "VI", "VI", "VI", "VI", "VI", 
"VI", "VI", "VI", "VI", "VI", "VI", "VI", "VI", "VI", "VI", "VI", 
"UY", "UY", "UY", "UY", "UY", "UY", "UY", "UY", "UY", "UY", "UY", 
"UY", "UY", "UY", "UY", "UY", "UY", "UY", "UY", "UY", "UY", "UY", 
"UY", "UY", "UY", "UY", "UY", "UY", "UY", "UY", "UY", "UY", "UY", 
"UZ", "UZ", "UZ", "UZ", "UZ", "UZ", "UZ", "UZ", "UZ", "UZ", "UZ", 
"UZ", "UZ", "UZ", "UZ", "UZ", "UZ", "UZ", "UZ", "UZ", "UZ", "UZ", 
"UZ", "UZ", "UZ", "UZ", "UZ", "UZ", "UZ", "UZ", "UZ", "UZ", "VU", 
"VU", "VU", "VU", "VU", "VU", "VU", "VU", "VU", "VU", "VU", "VU", 
"VU", "VU", "VU", "VU", "VU", "VU", "VU", "VU", "VU", "VU", "VE", 
"VE", "VE", "VE", "VE", "VE", "VE", "VE", "VE", "VE", "VE", "VE", 
"VE", "VE", "VE", "VE", "VE", "VE", "VE", "VE", "VE", "VE", "VE", 
"VE", "VE", "VE", "VE", "VE", "VE", "VE", "VE", "VE", "VE", "VE", 
"VN", "VN", "VN", "VN", "VN", "VN", "VN", "VN", "VN", "VN", "VN", 
"VN", "VN", "VN", "VN", "VN", "VN", "VN", "VN", "VN", "VN", "VN", 
"VN", "VN", "VN", "VN", "VN", "VN", "VN", "WF", "WF", "WF", "WF", 
"WF", "WF", "WF", "WF", "EH", "EH", "EH", "EH", "EH", "EH", "EH", 
"EH", "EH", "EH", "EH", "EH", "EH", "EH", "EH", "EH", "YE", "YE", 
"YE", "YE", "YE", "YE", "YE", "YE", "YE", "YE", "YE", "YE", "YE", 
"YE", "YE", "YE", "YE", "YE", "YE", "YE", "YE", "YE", "YE", "YE", 
"YE", "YE", "YE", "YE", "YE", "YE", "YE", "YE", "YE", "YE", "YE", 
"YE", "ZM", "ZM", "ZM", "ZM", "ZM", "ZM", "ZM", "ZM", "ZM", "ZM", 
"ZM", "ZM", "ZM", "ZM", "ZM", "ZM", "ZM", "ZM", "ZM", "ZM", "ZM", 
"ZM", "ZM", "ZM", "ZM", "ZM", "ZM", "ZM", "ZM", "ZM", "ZM", "ZM", 
"ZM", "ZM", "ZM", "ZM", "ZW", "ZW", "ZW", "ZW", "ZW", "ZW", "ZW", 
"ZW", "ZW", "ZW", "ZW", "ZW", "ZW", "ZW", "ZW", "ZW", "ZW", "ZW", 
"ZW", "ZW", "ZW", "ZW", "ZW", "ZW", "ZW", "ZW", "ZW", "ZW", "ZW", 
"ZW", "ZW", "ZW", "ZW", "ZW", "ZW"), Year = c(2005, 2005, 2005, 
2005, 2005, 2005, 2005, 2005, 2010, 2010, 2010, 2010, 2010, 2010, 
2010, 2010, 2015, 2015, 2015, 2015, 2015, 2015, 2015, 2015, 2020, 
2020, 2020, 2020, 2020, 2020, 2020, 2020, 2022, 2022, 2022, 2022, 
2005, 2005, 2005, 2005, 2005, 2005, 2005, 2005, 2010, 2010, 2010, 
2010, 2010, 2010, 2010, 2015, 2015, 2015, 2015, 2015, 2015, 2015, 
2015, 2020, 2020, 2020, 2020, 2020, 2020, 2020, 2020, 2022, 2022, 

"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", NA, NA, NA, NA, 
NA, NA, NA, NA, "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", NA, NA, NA, NA, NA, NA, NA, NA, "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", NA, NA, 
NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", NA, NA, NA, NA, NA, NA, NA, NA, "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, 
NA, NA, "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, 
NA, NA, NA, NA, NA, NA, "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", NA, NA, NA, NA, NA, NA, NA, NA, "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
NA, NA, NA, NA, NA, NA, NA, NA, "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
NA, NA, NA, NA, NA, NA, NA, NA, "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", NA, NA, NA, 
NA, NA, NA, NA, NA, "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "Not classified", "Not classified", 
"Not classified", "Not classified", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", "IBRD", 
"IBRD", "IBRD", "IBRD", NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, 
NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", 
"IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "IDA", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend", "Blend", 
"Blend", "Blend", "Blend", "Blend", "Blend", "Blend")), row.names = c(NA, 
-6673L), class = c("tbl_df", "tbl", "data.frame"))
```

```{r}
df
```

### Reading From Clipboard

```{r}
temp <- read_delim(clipboard())
temp
```

```{r eval = FALSE}
library(readxl)
df_migrants <- read_excel("data/un/Intentional homicide victims by sex, counts and ra.xls", sheet = 1)
```

## Transforming Data

### Combining Two Tables

-   left_join, etc

## Modeling

-   searching models: few numbers

-   linear regression

### Examples

-   gini, s80/s20

## References

-   Data Analysis for Researchers. [[Link](https://icu-hsuzuki.github.io/da4r/)]

-   H. Wickham. *R for Data Science (2e)*. [[Link](https://r4ds.hadley.nz)]・[[O'REILLY](https://www.oreilly.com/library/view/r-for-data/9781492097396/)].

    -   Data transformation [[Link](https://r4ds.hadley.nz/data-transform)]

    -   Data tidying [[Link](https://r4ds.hadley.nz/data-tidy)]

    -   Data import [[Link](https://r4ds.hadley.nz/data-import)]

    -   Import [[Link](https://r4ds.hadley.nz/import)]

-   Posit Recipes（New edition of Posit Primers）: interactive exercises [[Link](https://posit.cloud/learn/recipes)]

-   Cheat Sheet. [[Site Link](https://rstudio.github.io/cheatsheets/)]

    -   Data import with the tidyverse [[Link](https://rstudio.github.io/cheatsheets/html/data-import.html)]

    -   Data transformation with dplyr [[Link](https://rstudio.github.io/cheatsheets/html/data-transformation.html)]

-   dplyr: A Grammar of Data Manipulation [[Link](https://CRAN.R-project.org/package=dplyr)]

    -   Two-table verbs [[Link](https://cran.r-project.org/web/packages/dplyr/vignettes/two-table.html)]

-   swirl: `install.packages("swirl")` `libray(swirl)`, and `swirl()` after `rm(list=ls())`

## 
