---
title: "Week Four Assignment - EDA with WDI"
author: "ID Last, First"
date: "`r Sys.Date()`"
output:
  html_notebook: default
---

## Week Four Assignment

Choose at least two *similar* WDI codes with the *same scale*, and analyze the data.

-   Create an R Notebook of a data analysis containing the following and submit the rendered file (e.g., `w4_g123456.nb.html`) in Moodle.

    1.  Create an R Notebook using the R Notebook Template in Moodle and save it as `w4_g123456.Rmd`.

    2.  Edit author with name, ID, and title.

```{=html}
<!-- -->
```
-   Contents should include the following:

    -   A short abstract

    -   Information of data including data name, data code (or id), description

    -   Data including at least two indicators and a long table created using `pivot_longer`

    -   A line graph using the long table with a color aesthetic to depict at least two indicators in a chart.

    -   Several charts: a bar graph or a column graph, a histogram, a line graph, a scatter plot

    -   Observations or questions for visualizations

-   Include a choropleth map, if possible. (a challenge, not required)

-   Run each code block and preview to create `w4_g123456.nb.html`.

    -   Or, Run All under Run and Preview to check in your web browser!

    -   You can also view your file (e.g. `w4_g123456.nb.html`) by opening it from your web browser.

Submit your R Notebook file (w4_g123456.nb.html) in Moodle (Week Four Assignment).

***Due Sunday 21, January 2024, 11:59 PM***

# Your Project

## Title of your project

*The title can be in the title in YAML.*

### Short Abstract

We study .....

### About Data

1.  Name of the indicator 1: Indicator Code 1

-   Description:

2.  Name of the indicator 2: Indicator Code 2

-   Description:

3.  ...

### Set up

```{r}
library(tidyverse)
library(WDI)
```

*Create data folder if you do not have it under Files.*

```{r eval=FALSE}
dir.create("data")
```

*If you do not have `wdicache.rds` in your data folder, run the following two code chunks.*

```{r wdicache, eval=FALSE}
wdicache <- WDIcache()
```

```{r writewdicache, eval=FALSE, echo=FALSE}
write_rds(wdicache, "data/wdicache.rds")
```

```{r readwdicache, echo=FALSE}
wdicache <- read_rds("data/wdicache.rds")
```

### Importing Data

Edit short_name_1, chosen_indicator_1, short_name_2, chosen_indicator_2, etc. You can edit `df_yourdata` to a descriptive name. If you edit `df_yourdata` , please edit other parts as well.

```{r}
df_yourdata <- WDI(
  indicator = c(short_name_1 = chosen_indicator_1,
                short_name_2 = chosen_indicator_2),
  extra = TRUE, cache = wdicache)
```

```{r}
write_csv(df_yourdata, "data/yourdata.csv")
```

```{r}
df_yourdata <- read_csv("data/yourdata.csv")
```

### Viewing data

```{r}

```

```{r}

```

### Creating a long table

#### Example.

```         
df_sec_ter_gdp_long <- df_sec_ter_gdp |> 
  pivot_longer(cols = c(secondary, tertiary)) 
df_sec_ter_gdp_long
```

```{r}

```

### Visualizing data

```{r}

```

**Observations and Questions:**

-   

```{r}

```

**Observations and Questions:**

-   

```{r}

```

**Observations and Questions:**

-   

### A choropleth map

If possible, create a choropleth map. (a challenge, not required)

```{r}

```

**Observations and Questions:**

-   
