---
title: "GS Macro 2023"
output: html_notebook
---

# Datascience for Macroeconomics using WDI

## Introduction

### Datascience

Datascience is an interdisciplinary academic field to extract or extrapolate knowledge and insights from noisy, structured, and unstructured data.

Why datascience? There are many reasons, but I believe it would promote evidence based, non-biased thinking.

#### Exploratory Data Analysis, EDA

EDA is an iterative cycle that helps you understand what your data says. When you do EDA, you:

1.  Generate questions about your data

2.  Search for answers by visualising, transforming, and/or modeling your data

3.  Use what you learn to refine your questions and/or generate new questions

EDA is an important part of any data analysis. You can use EDA to make discoveries about the world; or you can use EDA to ensure the quality of your data, asking questions about whether the data meets your standards or not. (Posit Primers: [EDA](https://posit.cloud/learn/primers/3.1))

### Macroeconomics

The study of the entire economy of a region, a country, or the entire world

### World Development Indicators

World Development Indicators (WDI) is the World Bank\'s premier compilation of international statistics on global development. Drawing from officially recognized sources and including national, regional, and global estimates, the WDI provides access to approximately 1,600 indicators for 217 economies, with some time series extending back more than 50 years. The database helps users find information related to development, both current and historical. The topics covered in the WDI range from poverty, health, and demographics to GDP, trade, and the environment.

The World Development Indicators website provides access to data as well as information about data coverage, curation, and methodologies, and allows users to discover what type of indicators are available, how they are collected, and how they can be visualized to analyze development trends. (Wikipedia: [Link](https://en.wikipedia.org/wiki/World_Development_Indicators))

## Open Data and Public Data

Datascience and Artificial Intelligence

-   Computer Resources

-   Data

    -   Big Data

    -   Open and Public Data

> **Q. Explain 'Open Data' and 'Public Data', and their differences.**
>
> **A. AI Poe Assistant**. ([Poe.com](https://poe.com))
>
> "Open data" and "public data" are related concepts that refer to different aspects of data accessibility and usage.
>
> Open Data: Open data refers to the idea that certain data should be freely available to the public, without restrictions on access, usage, or redistribution. Open data is typically released in a machine-readable format, such as CSV, JSON, or XML, and is accompanied by an open license that allows anyone to use, reuse, and distribute the data for any purpose. The goal of open data is to promote transparency, collaboration, and innovation by enabling individuals, organizations, and communities to analyze and build upon the data.
>
> Open data often includes government data, scientific research data, public records, and other datasets that are deemed to be of public interest. Governments, international organizations, and various institutions actively promote the release of open data to foster accountability, drive economic growth, and empower citizens to make informed decisions.
>
> Public Data: Public data, on the other hand, refers to any data that is accessible or available to the public. It is a broader term that encompasses both open data and other types of data that may have certain restrictions on access or usage. Public data can include information that is freely and openly available, as well as data that is accessible through specific channels, such as public libraries, government agencies, or subscription-based services.
>
> Public data can include a wide range of information, such as government reports, census data, legal documents, financial statements, and more. While public data may be accessible to the public, it does not necessarily guarantee the same level of openness, usability, or freedom as open data. Public data may have limitations on its usage, copyright restrictions, or conditions imposed by the data provider.
>
> In summary, open data specifically refers to data that is freely accessible, usable, and redistributable without restrictions, often accompanied by an open license. Public data, on the other hand, is a broader term that includes both open data and other data that may have varying degrees of accessibility and usage restrictions.

#### World Bank on Open Data for Open Government

Visit [Open Government Data Toolkit](https://opendatatoolkit.worldbank.org/en/data/opendatatoolkit/home).

## R on RStudio

### Posit Cloud

-   Posit.cloud: <https://posit.cloud/>

    -   [Posit Primers](https://posit.cloud/learn/primers): interactive tutorials

    -   [Cheatsheets](https://posit.cloud/learn/cheat-sheets): RStudio IDE, Data Visualization, Data Transformation, Data Import, RMarkdown, etc.

-   Shared Project: <https://posit.cloud/content/5539763>

-   Create Your Copy and Download it.

## Datascience Workflow

![*The image above is from [R4DS(2e)](https://r4ds.hadley.nz) by Hadley Wickham, Mine Çetinkaya-Rundel and Garrett Grolemund*](data/data-science.png)

## First Datascience

We use two packages, `tidyverse` and `WDI`.

R packages are extensions to the R statistical programming language. R packages contain code, data, and documentation in a standardized collection format that can be installed by users of R, typically via a centralized software repository such as CRAN (the Comprehensive R Archive Network). [[CRAN Link](https://cran.r-project.org)]

-   **tidyverse**: The tidyverse is a collection of open source packages for the R programming language introduced by Hadley Wickham and his team that "share an underlying design philosophy, grammar, and data structures" of tidy data. Characteristic features of tidyverse packages include extensive use of non-standard evaluation and encouraging piping. [[CRAN Link](https://cran.r-project.org/web/packages/tidyverse/index.html)]

-   **WDI**: Search and download data from over 40 databases hosted by the World Bank, including the World Development Indicators ('WDI'), International Debt Statistics, Doing Business, Human Capital Index, and Sub-national Poverty indicators. [[CRAN Link](https://cran.r-project.org/web/packages/WDI/index.html)]

### Setup

Step 1. Install packages if necessary.

```{r eval = FALSE}
install.packages("tidyverse")
install.packages("WDI")
```

Step 2. Load packages.

```{r}
library(tidyverse)
library(WDI)
```

Step 3. Create a data directory for the first time.

```{r create-dirs, eval = FALSE}
dir.create("data")
```

Step 4. Set 'System Language' to be English, recommended.

```{r eval = FALSE}
Sys.setenv(LANG = "en")
```

### Importing GDP Data

The following code chunk is to download GDP data with the following indicator code.

WDI indicator: NY.GDP.MKTP.PP.KD

```{r cache = TRUE, eval = FALSE}
df_gdp <- WDI(indicator = "NY.GDP.MKTP.PP.KD")
```

N.B. There are many GDP related data in WDI, for example, "NY.GDP.MKTP.CD"

To avoid the internet traffic, save the data and reuse it.

CSV: comma separated values, a text format of a data.

```{r eval = FALSE}
write_csv(df_gdp, "data/gdp.csv")
```

Run codes above only once to download and write the data into the data directory.

```{r}
df_gdp <- read_csv("data/gdp.csv")
```

### Viewing Data

First, look at the data by `head`, `str` ucture, and `summary`.

`head`: display the first 6 rows by default

```{r}
head(df_gdp)
```

2.561800e+12 is in scientific notation, i.e., $2.561800 \times10^{12} = 2,562,800,000,000$.

`str`: display the structure of an object

```{r}
str(df_gdp)
```

`summary`: display the summary of an object

```{r}
summary(df_gdp)
```

In RNotebook, the following also displays the first 1000 rows of the data in the paged format.

```{r eval = FALSE}
df_gdp
```

### Transformation

`|>` , or `%>%`, is called a pipe operator and `df_gdp |> filter(country == COUNTRY)` is same as

`filter(df_gdp, country == COUNTRY)` .

`filter` : Keep rows that match a condition

```{r}
COUNTRY <- "Japan"
df_gdp |> filter(country == COUNTRY)
```

### Visualization

#### GDP of Japan

`ggplot() + geom_line()`: A tidyverse function of draw a line graph

`aes(year, NY.GDP.MKTP.PP.KD)` : aesthetic mapping sending year to x-axis and `NY.GDP.MKTP.PP.KD` to y-axis

```{r}
COUNTRY <- "Japan"
df_gdp |> filter(country == COUNTRY) |>
  ggplot(aes(year, NY.GDP.MKTP.PP.KD)) + geom_line()
```

Let's delete the rows with missing values using `drop_na(NY.GDP.MKTP.PP.KD)`. a transformation.

```{r}
COUNTRY <- "Japan"
df_gdp |> filter(country == COUNTRY) |> drop_na(NY.GDP.MKTP.PP.KD) |>
  ggplot(aes(year, NY.GDP.MKTP.PP.KD)) + geom_line()
```

#### GDP of the World

```{r}
COUNTRY <- "World"
df_gdp |> filter(country == COUNTRY) |>
  ggplot(aes(year, NY.GDP.MKTP.PP.KD)) + geom_line()
```

#### Exercise.

1.  Delete the missing data of the GDP of the World by mimicking the one of Japan.
2.  Write down your observations and questions.

```{r eval = FALSE}
COUNTRY <- "World"
df_gdp |> filter(country == COUNTRY) |>
  ggplot(aes(year, NY.GDP.MKTP.PP.KD)) + geom_line()
```

**Observations and Questions**

-   e.g. The GDP of the world is continuously increasing since 1990.

-   

#### GDP of the countries

By country names

```{r}
COUNTRIES <- c("Japan", "China", "India", "United Kingdom", "United States", "Germany", "France")
df_gdp |> filter(country %in% COUNTRIES) |> drop_na(NY.GDP.MKTP.PP.KD) |>
  ggplot(aes(year, NY.GDP.MKTP.PP.KD, color = country)) + geom_line()
```

```{r}
ISO2C <- c("JP", "CN", "ID", "UK", "US", "DE", "FR")
df_gdp |> filter(iso2c %in% ISO2C) |> drop_na(NY.GDP.MKTP.PP.KD) |>
  ggplot(aes(year, NY.GDP.MKTP.PP.KD, color = iso2c)) + geom_line()
```

#### Exercise.

What happens if you replace `color = iso2c` at the bottom of the code above with `colour = iso2c` , `color = country` , `col = country` ?

```{r eval = FALSE}
ISO2C <- c("JP", "CN", "ID", "UK", "US", "DE", "FR")
df_gdp |> filter(iso2c %in% ISO2C) |> drop_na(NY.GDP.MKTP.PP.KD) |>
  ggplot(aes(year, NY.GDP.MKTP.PP.KD, color = iso2c)) + geom_line()
```

#### List of Countries and iso2c

```{r}
df_gdp |> distinct(country, iso2c)
```

#### **Exercise.**

Set COUNTRIES and/or ISO2C to draw line graphs of GDP.

```{r eval = FALSE}
COUNTRIES <- c() # surround the country name with quotation marks, and use a comma as a separator
df_gdp |> filter(country %in% COUNTRIES) |> drop_na(NY.GDP.MKTP.PP.KD) |>
  ggplot(aes(year, NY.GDP.MKTP.PP.KD, color = country)) + geom_line()
```

```{r eval = FALSE}
ISO2C <- c() # surround the iso2c code with quotation marks, and use a comma as a separator
df_gdp |> filter(iso2c %in% ISO2C) |> drop_na(NY.GDP.MKTP.PP.KD) |>
  ggplot(aes(year, NY.GDP.MKTP.PP.KD, color = iso2c)) + geom_line()
```

# World Development Indicators

## Find Indicator Codes

1.  World Bank Home Page

    -   World Development Indicators: [Link](https://datatopics.worldbank.org/world-development-indicators/)

    -   World Bank Open Data: [Link](https://data.worldbank.org)

    -   WDI Statistical Tables: [Link](https://wdi.worldbank.org/tables)

2.  Excel Files

    -   Data Catalogues: [Link](https://datacatalog.worldbank.org/search/dataset/0037712/World-Development-Indicators) Download Excel File

3.  API Search

```{r}
WDIsearch(string = "gdp", field = "name")
```

```{r}
WDIsearch(string = "NY.GDP.MKTP.PP.KD", field = "indicator", short = FALSE)
```

#### Assignment

1.  Find at least one WDI indicator with its name and its code.

2.  Find at least one pair of WDI indicators with their names and their codes you want to study their relation.

## GDP and GDP per Capita

1.  GDP, PPP (constant 2017 international \$): NY.GDP.MKTP.PP.KD

2.  Population, total: SP.POP.TOTL

3.  Calculate GDP per Capita

    -   GDP per capita, PPP (constant 2017 international \$): NY.GDP.PCAP.PP.KD

-   GDP, PPP (constant 2017 international \$) PPP GDP is gross domestic product converted to international dollars using purchasing power parity rates. An international dollar has the same purchasing power over GDP as the U.S. dollar has in the United States. GDP is the sum of gross value added by all resident producers in the country plus any product taxes and minus any subsidies not included in the value of the products. It is calculated without making deductions for depreciation of fabricated assets or for depletion and degradation of natural resources. Data are in constant 2017 international dollars. ID: NY.GDP.MKTP.PP.KD

-   Population, total Total population is based on the de facto definition of population, which counts all residents regardless of legal status or citizenship. The values shown are midyear estimates. ID: SP.POP.TOTL

```{r cache = TRUE, eval = FALSE}
df_gdppcap <- WDI(indicator = c(gdp = "NY.GDP.MKTP.PP.KD", pop = "SP.POP.TOTL", gdppcap = "NY.GDP.PCAP.PP.KD"), extra = TRUE)
```

```{r eval = FALSE}
write_csv(df_gdppcap, "data/gdppcap.csv")
```

```{r}
df_dgppcap <- read_csv("data/gdppcap.csv")
```

```{r}
COUNTRY <- "World"
df_gdppcap |> filter(country == COUNTRY) |>
  ggplot(aes(year, gdppcap)) + geom_line()
```

```{r}
COUNTRY <- "World"
df_gdppcap |> filter(country == COUNTRY) |>
  ggplot(aes(year, pop)) + geom_line()
```

#### Exercise.

Write your observations and questions.

### GDP Per Capita

```{r}
df_gdppcap2 <- df_gdppcap |> drop_na(pop) |> 
  mutate(PCAP = gdp/pop, .after = gdppcap)
```

```{r}
df_gdppcap2
```

#### Check against GDP per capita, PPP

```{r eval = FALSE}
df_gdppcap2 |> drop_na(gdppcap, PCAP) |> mutate(near = near(gdppcap, PCAP)) |> 
  summarize(numberofdata = n(), sum(near))
```

```{r}
df_gdppcap2 |> filter(!near(gdppcap, PCAP))
```

#### Exercise.

Write your observations and questions.

### Visualization

Two useful questions.

1.  What type of **variation** occurs **within** my variables?

2.  What type of **covariation** occurs **between** my variables?

See [Link](https://posit.cloud/learn/primers/3.1).

#### Ranks.

`arrange(desc(gdp))` is to reorder in descending order of `gdp,` `arrange(gdp)` in ascending order.

```{r}
df_gdppcap |> filter(year == 2022, region != "Aggregates") |> 
  drop_na(gdp) |> arrange(desc(gdp))
```

#### Exercises.

1.  Find the top 10 of the countries with the highest GDP per capita.

2.  Find the top 10 of the countries with the lowest GDP per capita.

3.  Find the top 10 of the countries with the largest population.

4.  Find the top 10 of the countries with the smallest population.

#### Variation 1. Histogram

```{r}
df_gdppcap |> filter(year == 2022, region != "Aggregates") |> drop_na(gdp) |> 
  ggplot(aes(gdp)) + geom_histogram()
```

```{r}
df_gdppcap |> filter(year == 2022, region != "Aggregates") |> drop_na(gdppcap) |> 
  ggplot(aes(gdppcap)) + geom_histogram()
```

```{r}
df_gdppcap |> filter(year == 2022, region != "Aggregates") |> drop_na(gdp) |> 
  ggplot(aes(gdp)) + geom_histogram() + scale_x_log10()
```

#### Exercises.

1.  Change bins, i.e., `geom_histogram(bins = 20)`, etc.

```{r eval = FALSE}
df_gdppcap |> filter(year == 2022, region != "Aggregates") |> drop_na(gdp) |> 
  ggplot(aes(gdp)) + geom_histogram(bins = 20) + scale_x_log10()
```

2.  Create a similar histogram of gdppcap by using `scale_x_log10()` and adjust the number of bins.

```{r eval = FALSE}
df_gdppcap |> filter(year == 2022, region != "Aggregates") |> drop_na(gdppcap) |> 
  ggplot(aes(gdppcap)) + geom_histogram() + scale_x_log10()
```

3.  Create a similar histogram for population.
4.  Write your observations and comments.

#### Extra.

```{r}
df_gdppcap |> filter(year == 2022,region != "Aggregates") |> drop_na(pop) |> 
  ggplot(aes(pop)) + geom_histogram() + scale_x_log10()
```

#### Variation 2. Boxplot

```{r}
df_gdppcap2 |> filter(year == 2020) |> drop_na(gdppcap) |> 
  ggplot(aes(gdppcap)) + geom_boxplot() + scale_x_log10()
```

```{r}
df_gdppcap2 |> filter(year == 2020) |> drop_na(gdppcap) |> 
  filter(income != "Aggregates") |> 
  ggplot(aes(gdppcap, income, fill = income)) + geom_boxplot() + scale_x_log10() +
  theme(legend.position = "none")
```

```{r}
df_gdppcap2 |> filter(year == 2020) |> drop_na(gdp) |> 
  filter(income != "Aggregates") |> 
  ggplot(aes(gdp, region, fill = region)) + geom_boxplot() + scale_x_log10() +
  theme(legend.position = "none")
```

```{r}
df_gdppcap2 |> filter(year == 2020, region !="Aggregates") |> drop_na(gdp, pop) |> 
  ggplot(aes(pop, gdp, color = region)) + geom_point() + 
  scale_x_log10() + scale_y_log10()
```

```{r eval = FALSE}
install.packages("plotly")
```

```{r}
library(plotly)
test <- df_gdppcap2 |> filter(year == 2020, region !="Aggregates") |> drop_na(gdp, pop) |> 
  ggplot(aes(color = country, shape = region, pop, gdp)) + geom_point() + 
  scale_x_log10() + scale_y_log10() + theme(legend.position = "none")
test |> ggplotly()
```

## CO2 Emissions Per Capita vs GDP Per Capita

1.  CO2 emissions (metric tons per capita): EN.ATM.CO2E.PC

2.  GDP per capita, PPP (constant 2017 international \$): NY.GDP.PCAP.PP.KD

-   CO2 emissions (metric tons per capita) Carbon dioxide emissions are those stemming from the burning of fossil fuels and the manufacture of cement. They include carbon dioxide produced during consumption of solid, liquid, and gas fuels and gas flaring. EN.ATM.CO2E.PC

-   GDP per capita, PPP (constant 2017 international \$) GDP per capita based on purchasing power parity (PPP). PPP GDP is gross domestic product converted to international dollars using purchasing power parity rates. An international dollar has the same purchasing power over GDP as the U.S. dollar has in the United States. GDP at purchaser's prices is the sum of gross value added by all resident producers in the country plus any product taxes and minus any subsidies not included in the value of the products. It is calculated without making deductions for depreciation of fabricated assets or for depletion and degradation of natural resources. Data are in constant 2017 international dollars. ID: NY.GDP.PCAP.PP.KD

```{r cache = TRUE}
df_co2gdp <- WDI(indicator = c(co2pcap = "EN.ATM.CO2E.PC", gdppcap = "NY.GDP.PCAP.PP.KD"), extra = TRUE)
```

```{r}
write_csv(df_co2gdp, "data/co2gdp.csv")
```

```{r eval=FALSE}
df_co2gdp <- read_csv("data/co2gdp.csv")
```

```{r}
COUNTRY <- "World"
df_co2gdp |> filter(country == COUNTRY) |>
  ggplot(aes(year, co2pcap)) + geom_line()
```

```{r}
df_co2gdp |> filter(year == 2020) |> drop_na(co2pcap) |>
  ggplot(aes(gdppcap, co2pcap)) + geom_point()
```

```{r}
df_co2gdp |> filter(year == 2020) |> 
  drop_na(gdppcap, co2pcap) |>
  ggplot(aes(gdppcap, co2pcap)) + geom_point() +
  scale_x_log10() + scale_y_log10()
```

```{r}
df_co2gdp |> filter(year == 2020) |> 
  drop_na(gdppcap, co2pcap) |>
  ggplot(aes(gdppcap, co2pcap)) + geom_point() +
  geom_smooth(method = "lm", formula = 'y~x', se = FALSE) +
  scale_x_log10() + scale_y_log10()
```

```{r}
df_co2gdp |> lm(co2pcap~gdppcap, data = _) |> summary()
```

## School Enrollment vs GDP Per Capita

1.  School enrollment, secondary (% gross): SE.SEC.ENRR

2.  GDP per capita, PPP (constant 2017 international \$): NY.GDP.PCAP.PP.KD

-   School enrollment, secondary (% gross) Gross enrollment ratio is the ratio of total enrollment, regardless of age, to the population of the age group that officially corresponds to the level of education shown. Secondary education completes the provision of basic education that began at the primary level, and aims at laying the foundations for lifelong learning and human development, by offering more subject- or skill-oriented instruction using more specialized teachers. SE.SEC.ENRR

-   GDP per capita, PPP (constant 2017 international \$) GDP per capita based on purchasing power parity (PPP). PPP GDP is gross domestic product converted to international dollars using purchasing power parity rates. An international dollar has the same purchasing power over GDP as the U.S. dollar has in the United States. GDP at purchaser's prices is the sum of gross value added by all resident producers in the country plus any product taxes and minus any subsidies not included in the value of the products. It is calculated without making deductions for depreciation of fabricated assets or for depletion and degradation of natural resources. Data are in constant 2017 international dollars. ID: NY.GDP.PCAP.PP.KD

```{r cache = TRUE}
df_secgdp <- WDI(indicator = c(sec = "SE.SEC.ENRR", gdppcap = "NY.GDP.PCAP.PP.KD"), extra = TRUE)
```

```{r}
write_csv(df_secgdp, "data/secgdp.csv")
```

```{r eval=FALSE}
df_secgdp <- read_csv("data/secgdp.csv")
```

```{r}
COUNTRY <- "World"
df_secgdp |> filter(country == COUNTRY) |>
  ggplot(aes(year, sec)) + geom_line()
```

```{r}
df_secgdp |> filter(year == 2020) |> drop_na(sec) |>
  ggplot(aes(gdppcap, sec)) + geom_point()
```

```{r}
df_secgdp |> filter(year == 2020) |> drop_na(gdppcap, sec) |>
  ggplot(aes(gdppcap, sec)) + geom_point() +
  scale_x_log10()
```

```{r}
df_secgdp |> filter(year == 2020) |> drop_na(gdppcap, sec) |>
  ggplot(aes(gdppcap, sec)) + geom_point() +
  geom_smooth(method = "lm", formula = 'y~x', se = FALSE) +
  scale_x_log10()
```

```{r}
df_secgdp |> lm(sec~gdppcap, data = _) |> summary()
```

## References

1.  R for Data Science (2e): [Link](https://r4ds.hadley.nz). The First Edition: [Link](https://r4ds.had.co.nz).

2.  Posit Primers: [Link](https://posit.cloud/learn/primers).

3.  Cheat Sheet: [Link](https://posit.cloud/learn/cheat-sheets).

4.  Input data set: Historical country-level Gross Domestic Product (GDP): [Link](https://www.isimip.org/gettingstarted/input-data-bias-adjustment/details/33/)
