---
title: "Gini Coefficients and GDP Growth"
output:
  pdf_document: default
  html_notebook: default
---

# Setup

If you have installed the package "tidyverse", you do not need to run the next code chunk.

```{r eval = FALSE}
install.packages("tidyverse")
```

Although "readxl" and "broom" are part of the package "tidyverse', you need to load separately as they are not core and not loaded with 'tidyverse'.

```{r}
library(tidyverse)
library(readxl) # a package for Excel files, a part of tidyverse but not core
library(broom) # a package for modeling, a part of tidyverse but not core
library(WDI)
```

# Importing

For Excel, you need to specify wich sheet you want to import by name as below or the number. You also need to skip several rows when blank rows are included.

```{r warning = FALSE}
df_gini_gdpgrowth_orig <- read_excel("data/P_Data_Extract_From_World_Development_Indicators 20 years db.xlsx", 
    col_types = c("text", "text", "text", 
        "text", "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric"), na = "\t ..", n_max = 532)
```

Check the data frames.

```{r}
df_gini_gdpgrowth_orig |> head()
```

```{r}
df_gini_gdpgrowth2 <- WDI(indicator = c(gini = "SI.POV.GINI", gdpgrowth = "NY.GDP.MKTP.KD.ZG"))
df_gini_gdpgrowth2 |> head()
```


# Tidying

After tidying the original data, we obtained about the same as the one obtained above using WDI package. So I recommend you to get the data using WDI.

```{r}
df_gini_gdpgrowth <- df_gini_gdpgrowth_orig |> pivot_longer(5:24, names_to = "year", values_to = "value") |>
  mutate(year = as.numeric(str_sub(year, 1, 4))) |> select(-4) |> 
  pivot_wider(names_from = `Series Name`, values_from = value)
df_gini_gdpgrowth |> head()
```

# Number of available data

```{r}
df_gini_gdpgrowth2 |> drop_na(gini, gdpgrowth) |> 
  ggplot(aes(year)) + geom_bar()
```

# Scatter Plots

It is better to fix a year.

```{r}
YEAR <- 2018
df_gini_gdpgrowth2 |> filter (year == YEAR) |> drop_na(gini, gdpgrowth) |>
  ggplot(aes(gini, gdpgrowth)) + geom_point() + geom_smooth(method = "lm", formula = y~x, se = FALSE)
```

# Models


```{r}
YEAR <- 2018
model0 <- df_gini_gdpgrowth2 |> filter (year == YEAR) |> drop_na(gini, gdpgrowth) |> lm(gdpgrowth ~ gini, data = _) 
```

```{r}
model0 |> summary()
```

```{r}
model0 |> summary() |> glance()
```
```{r}
model0 |> summary() |> tidy()
```


```{r}
model0 |> augment() |> head()
```

